---
title: "Replication File India Paper: Impact of Air Pollution on Birth Outcomes"
author: "Shashank Misra"
date: "`r Sys.Date()`"
output: github_document
---


#Importing Main Dataset and Renaming Variables in Line with My regressions + All Packages
```{r}
library(tidyverse)
library(haven)
library(car)
library(writexl)
library(openxlsx)
library(scales)
library(sf)
library(sandwich)
library(skimr)
library(fixest)
library(readxl)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggforce)
library(lmtest)
library(stargazer)
library(stringr)
library(broom)
library(ggtext)
library(ggforce)
library(AER)
#Import DHS data here, linked to merra pollution and wind direction from ERA5 and already calculated in-utero weather/pm variables
FinalDataset <- read_dta("FinalDatasetNov18.dta") #Here use from the directory imported
FinalDataset <- FinalDataset %>% mutate(MOBMother=MOB, YOBMother=YOB) %>% filter(code!=543) #Lakshwadeep code 543 missing weather data
FinalDataset <- FinalDataset %>% select(-MOB,-YOB) #incorrect MOB AND YOB (is from mother not child hence do not need)
FinalDataset <- FinalDataset %>% mutate(tri_cumulative=pm_cumulative,avg_north_share_cumulative=North_share_cumulative, avg_east_share_cumulative=East_share_cumulative, avg_south_share_cumulative=South_share_cumulative, avg_temperature_cumulative=temp_cumulative, avg_wind_speed_cumulative=windspeed_cumulative, cooking=dirty_cookingfuel, female=if_else(sex_child == 2, 1, 0), brthwt=birthweight, LBW=lbw, VLBW=vlbw, bord=birthorder, age_birth=YOB_child-YOBMother,anemia=anemic, avg_west_share_cumulative=West_share_cumulative, YOB=YOB_child,MOB=MOB_child,religion=religion_code,minoritycastetribe=caste)  # No in-utero variables for 2009, hence filter 2010 after sept (NOW RESOLVED FULL DF AVAILABLE INCLUDING ALL 2009 BIRTHS)

```

#Give Summary Stats
```{r}

FinalDatasetSummary <- FinalDataset %>%
  mutate(
    # Religion dummies
    hindu = if_else(religion_code == 1, 1, 0),
    muslim = if_else(religion_code == 2, 1, 0),
    christian = if_else(religion_code == 3, 1, 0),
    other_religion = if_else(!(religion_code %in% c(1, 2, 3)), 1, 0),
    # Caste dummies
    scheduled_tribe = if_else(caste == 2, 1, 0),
    obc = if_else(caste == 3, 1, 0),
    scheduled_caste = if_else(caste == 1, 1, 0),
    other_caste = if_else(!(caste %in% c(1, 2, 3)), 1, 0),
    # Dirty fuel dummy based on v161
    dirty_fuel = cooking
  )


# Select all variables of interest
summary_vars <- FinalDatasetSummary %>%
  select(
    hindu, muslim, christian, other_religion,
    scheduled_tribe, obc, scheduled_caste, other_caste,
    dirty_fuel,
    sex_child, urban , bmi, wealth_index, anemia,
    birthorder, age_birth, MOB_child, YOB_child, lbw, vlbw, birthweight, tri_cumulative
  )



#Simple summary stats
summary(summary_vars)



```
#Baseline IV Results

```{r}
# First-stage regression (cumulative)
FinalDataset$religion <- as.factor(FinalDataset$religion)
FinalDataset$cooking <- as.factor(FinalDataset$cooking)
FinalDataset$minoritycastetribe <- as.factor(FinalDataset$minoritycastetribe)
FinalDataset$wealth_index <- as.factor(FinalDataset$wealth_index)
FinalDataset$anemia <- as.factor(FinalDataset$anemia)


FinalDatasetFiltered <- FinalDataset %>% filter(brthwt<5500,brthwt>900) 
FinalDataset$religion <- factor(FinalDataset$religion)

first_stage <- lm(
  tri_cumulative ~ avg_north_share_cumulative:factor(region) +
                   avg_east_share_cumulative:factor(region)  +   avg_south_share_cumulative:factor(region)  + avg_wind_speed_cumulative +religion+minoritycastetribe+cooking+female+urban+bmi+wealth_index+ anemia + +avg_temperature_cumulative+ factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

instr_vars <- grep("avg_north_share_cumulative|avg_east_share_cumulative|avg_south_share_cumulative", 
                   names(coef(first_stage)), value = TRUE)


# Save the predicted values of tri_cumulative
FinalDataset$tri_cumulative_hat <- predict(first_stage)

# Save the first-stage residuals
FinalDataset$first_stage_residuals <- residuals(first_stage)



### WITH CLUSTERED ROBUST F STAT



# Compute clustered robust standard errors at the district level
vcov_clustered <- vcovCL(first_stage, cluster = ~district_matched, type = "HC1") #note that district_matched can be interchanged with code essentially the same ID for municipalities (districts)

# Run Wald test using clustered SE
f_test_clustered <- linearHypothesis(first_stage, instr_vars, vcov = vcov_clustered)

# Display test results
print(f_test_clustered)

# Extract the clustered F-statistic
f_stat_clustered <- f_test_clustered$F[2]
print(f_stat_clustered)


# Display results with clustered standard errors
summary_clusteredfirststage <- coeftest(first_stage, vcov. = vcov_clustered)

```




```{r}


library(sandwich)
library(lmtest)
library(stargazer)
# Second-stage regression (cumulative)
# Define the Tropic of Cancer latitude as a dividing line
tropic_of_cancer <- 23.5
FinalDatasetFiltered <- FinalDataset %>% filter(brthwt<5500,brthwt>900) %>% mutate(wood=ifelse(cooking==8,1,0))
FinalDatasetFilteredExtremes <- FinalDataset%>% filter(brthwt<5500,brthwt>900) 
FinalDatasetFilteredBord1 <- FinalDataset %>% filter(bord<2)
FinalDatasetFilteredCard <- FinalDataset %>% filter(card_recall==1)
FinalDatasetFilteredWealthTop <- FinalDataset %>% filter(wealth_index>3)
FinalDatasetFilteredWealthBottom <- FinalDataset %>% filter(wealth_index<3)
FinalDatasetFilteredUrban <- FinalDataset %>% filter(urban==1)
FinalDatasetFilteredRural <- FinalDataset %>% filter(urban!=1)
FinalDatasetFilteredHighPollution <- FinalDataset %>% filter(tri_cumulative>40)




second_stage <- lm(
    brthwt ~ tri_cumulative_hat + avg_temperature_cumulative  + avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth ,
  data = FinalDataset
)


cluster_se <- vcovCL(second_stage, cluster = ~district_matched, type='HC1')


summary_clustered <- coeftest(second_stage, vcov. = cluster_se)


stargazer(
  second_stage,
  se = list(sqrt(diag(cluster_se))),
  type = "text", omit='factor',
  title = "Second-Stage Regression with Clustered SE at District Level"
)

```

```{r}


LBWbaselineIV <- lm(
  LBW ~ tri_cumulative_hat + avg_temperature_cumulative  +
          avg_wind_speed_cumulative + minoritycastetribe + religion + cooking + female +
          urban + bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset)





VLBWbaselineIV <- lm(
  VLBW ~ tri_cumulative_hat + avg_temperature_cumulative  +
          avg_wind_speed_cumulative + minoritycastetribe + religion + cooking + female +
          urban + bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset 
)




cluster_se1 <- vcovCL(LBWbaselineIV, cluster = ~district_matched, type='HC1')
summary_clustered1 <- coeftest(LBWbaselineIV, vcov. = cluster_se1)



cluster_se2 <- vcovCL(VLBWbaselineIV, cluster = ~district_matched, type = "HC1")
summary_clustered2 <- coeftest(VLBWbaselineIV, vcov. = cluster_se2)


stargazer(
  LBWbaselineIV, VLBWbaselineIV,
  type = "text",
  title = "LBW VLBW IV BASELINE",
  omit = "factor",  
  star.cutoffs = c(0.1, 0.05, 0.01),digits=4  
)



```


#Exporting Baseline First Stage and Second Stage Results to Excel
`{r}

summary_dffirststage <- as.data.frame(summary_clusteredfirststage[,])
summary_dffirststage$Variable <- rownames(summary_clusteredfirststage)
summary_dfbw <- as.data.frame(summary_clustered[,])
summary_dfbw$Variable <- rownames(summary_clustered)
summary_dfLBW <- as.data.frame(summary_clustered1[,])
summary_dfLBW$Variable <- rownames(summary_clustered1)
summary_dfVLBW <- as.data.frame(summary_clustered2[,])
summary_dfVLBW$Variable <- rownames(summary_clustered2)



# Save each data frame to a separate Excel file
write_xlsx(summary_dffirststage, "first_stage_results.xlsx")
write_xlsx(summary_dfbw, "birth_weight_results.xlsx")
write_xlsx(summary_dfLBW, "low_birth_weight_results.xlsx")
write_xlsx(summary_dfVLBW, "very_low_birth_weight_results.xlsx")




`


#OLS Results

```{r}

LBWFE <- lm(
  LBW ~ tri_cumulative + avg_temperature_cumulative  +
          avg_wind_speed_cumulative + minoritycastetribe + religion + cooking + female +
          urban + bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset)




VLBWFE <- lm(
  VLBW ~ tri_cumulative + avg_temperature_cumulative  +
          avg_wind_speed_cumulative + minoritycastetribe + religion + cooking + female +
          urban + bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset 
)



cluster_se1FE <- vcovCL(LBWFE, cluster = ~district_matched, type='HC1')
summary_clustered1FE <- coeftest(LBWFE, vcov. = cluster_se1FE)


cluster_se2FE <- vcovCL(VLBWFE, cluster = ~district_matched, type = "HC1")
summary_clustered2FE<- coeftest(VLBWFE, vcov. = cluster_se2FE)

second_stageFE <- lm(
    brthwt ~  tri_cumulative + avg_temperature_cumulative + avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + factor(region)+factor(MOB) + factor(YOB) + bord +age_birth,
  data = FinalDataset
)

cluster_seFE <- vcovCL(second_stageFE, cluster = ~district_matched,type='HC1')

summary_clusteredFE <- coeftest(second_stageFE, vcov. = cluster_seFE)

stargazer(
  second_stageFE,
  se = list(sqrt(diag(cluster_seFE))),
  type = "text", omit='factor',
  title = "Second-Stage Regression OLS with Clustered SE at District Level"
)


stargazer(
  LBWFE,VLBWFE,digits=5,
  se = list(sqrt(diag(cluster_se1FE)), sqrt(diag(cluster_se2FE))),
  type = "text", omit='factor',
  title = "OLS regs Clustered SE at District Level"
)

```
#Hausman Test OLS vs Baseline IV
```{r}

#Hausman BW
b_olsbw  <- summary_clusteredFE["tri_cumulative", "Estimate"]
se_olsbw <- summary_clusteredFE["tri_cumulative", "Std. Error"]

b_ivbw  <- summary_clustered["tri_cumulative_hat", "Estimate"]
se_ivbw <- summary_clustered["tri_cumulative_hat", "Std. Error"]
var_olsbw <- se_olsbw^2
var_ivbw  <- se_ivbw^2

H_statbw  <- (b_ivbw - b_olsbw)^2 / (var_ivbw - var_olsbw)
p_valuebw <- pchisq(H_statbw, df = 1, lower.tail = FALSE)

H_statbw
p_valuebw



#Hausman OLS IV LBW
b_olslbw  <- summary_clustered1FE["tri_cumulative", "Estimate"]
se_olslbw <- summary_clustered1FE["tri_cumulative", "Std. Error"]


b_ivlbw  <- summary_clustered1["tri_cumulative_hat", "Estimate"]
se_ivlbw <- summary_clustered1["tri_cumulative_hat", "Std. Error"]
var_olslbw <- se_olslbw^2
var_ivlbw  <- se_ivlbw^2

H_statlbw  <- (b_ivlbw - b_olslbw)^2 / (var_ivlbw - var_olslbw)
p_valuelbw <- pchisq(H_statlbw, df = 1, lower.tail = FALSE)

H_statlbw
p_valuelbw


# OLS / FE estimate (efficient under H0)
b_olsvlbw  <- summary_clustered2FE["tri_cumulative", "Estimate"]
se_olsvlbw <- summary_clustered2FE["tri_cumulative", "Std. Error"]

# IV estimate (always consistent)
b_ivvlbw  <- summary_clustered2["tri_cumulative_hat", "Estimate"]
se_ivvlbw <- summary_clustered2["tri_cumulative_hat", "Std. Error"]
var_olsvlbw <- se_olsvlbw^2
var_ivvlbw  <- se_ivvlbw^2

H_statvlbw  <- (b_ivvlbw - b_olsvlbw)^2 / (var_ivvlbw - var_olsvlbw)
p_valuevlbw <- pchisq(H_statvlbw, df = 1, lower.tail = FALSE)

H_statvlbw
p_valuevlbw


```



#Monotonicity 40 regions
#40
```{r}
first_stagenew40 <- lm(
  tri_cumulative ~ avg_north_share_cumulative:factor(regionnew40) +
                   avg_east_share_cumulative:factor(regionnew40) + 
                   avg_south_share_cumulative:factor(regionnew40) +
                   avg_temperature_cumulative  + avg_wind_speed_cumulative +religion+minoritycastetribe+cooking+female+urban+bmi+wealth_index+anemia + factor(regionnew40):factor(MOB) + factor(YOB)+bord+age_birth,
  data = FinalDataset
)



FinalDataset$tri_cumulative_hatnew40 <- predict(first_stagenew40)

FinalDataset$first_stage_residuals40 <- residuals(first_stagenew40)

second_stagenew40 <- lm(
    brthwt ~ tri_cumulative_hatnew40 + avg_temperature_cumulative  + avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + factor(regionnew40):factor(MOB) + factor(YOB) + bord +age_birth,
  data = FinalDataset
)


cluster_senew40<- vcovCL(second_stagenew40, cluster = ~district_matched,type='HC1')


summary_clusterednew40 <- coeftest(second_stagenew40, vcov. = cluster_senew40)




LBWIV40 <- lm(
  LBW ~ tri_cumulative_hatnew40 + avg_temperature_cumulative +
          avg_wind_speed_cumulative + minoritycastetribe + religion + cooking + female +
          urban + bmi + wealth_index + anemia + factor(regionnew40):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset)




VLBWIV40<- lm(
  VLBW ~ tri_cumulative_hatnew40 + avg_temperature_cumulative +
          avg_wind_speed_cumulative + minoritycastetribe + religion + cooking + female +
          urban + bmi + wealth_index + anemia + factor(regionnew40):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset  
)



cluster_se1new40 <- vcovCL(LBWIV40, cluster = ~district_matched, type='HC1')
summary_clustered1new40 <- coeftest(LBWIV40, vcov. = cluster_se1new40)


cluster_se2new40 <- vcovCL(VLBWIV40, cluster = ~district_matched, type = "HC1")
summary_clustered2new40<- coeftest(VLBWIV40, vcov. = cluster_se2new40)


stargazer(
  second_stagenew40,
  se = list(sqrt(diag(cluster_senew40))),
  type = "text", omit='factor',
  title = "Second-Stage Regression with Clustered SE at District Level"
)

stargazer(
  LBWIV40, VLBWIV40,
  se = list(sqrt(diag(cluster_se1new40)), sqrt(diag(cluster_se2new40))), digits=5,  
  type = "text",
  title = "40 REGION RESULTS",
  omit = "factor",  
  star.cutoffs = c(0.1, 0.05, 0.01)  
)




```

#50 Regions
```{r}
first_stagenew50 <- lm(
  tri_cumulative ~ avg_north_share_cumulative:factor(regionnew50) +
                   avg_east_share_cumulative:factor(regionnew50) + 
                   avg_south_share_cumulative:factor(regionnew50) +
                   avg_temperature_cumulative + avg_wind_speed_cumulative +religion+minoritycastetribe+cooking+female+urban+bmi+wealth_index+anemia + factor(regionnew50):factor(MOB) +factor(YOB)+bord+age_birth,
  data = FinalDataset
)



FinalDataset$tri_cumulative_hatnew50 <- predict(first_stagenew50)

FinalDataset$first_stage_residuals50 <- residuals(first_stagenew50)


second_stagenew50 <- lm(
    brthwt ~ tri_cumulative_hatnew50 + avg_temperature_cumulative + avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + factor(regionnew50):factor(MOB) + factor(YOB) + bord +age_birth,
  data = FinalDataset
)

cluster_senew50<- vcovCL(second_stagenew50, cluster = ~district_matched, type='HC1')


summary_clusterednew50 <- coeftest(second_stagenew50, vcov. = cluster_senew50)



LBWIV50 <- lm(
  LBW ~ tri_cumulative_hatnew50 + avg_temperature_cumulative  +
          avg_wind_speed_cumulative + minoritycastetribe + religion + cooking + female +
          urban + bmi + wealth_index + anemia + factor(regionnew50):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset)



VLBWIV50 <- lm(
  VLBW ~ tri_cumulative_hatnew50 + avg_temperature_cumulative  +
          avg_wind_speed_cumulative + minoritycastetribe + religion + cooking + female +
          urban + bmi + wealth_index + anemia + factor(regionnew50):factor(MOB) + factor(YOB) + bord + age_birth ,
  data = FinalDataset
)


cluster_se1new50 <- vcovCL(LBWIV50, cluster = ~district_matched, type='HC1')
summary_clustered1new50 <- coeftest(LBWIV50, vcov. = cluster_se1new50)


cluster_se2new50 <- vcovCL(VLBWIV50, cluster = ~district_matched, type = "HC1")
summary_clustered2new50<- coeftest(VLBWIV50, vcov. = cluster_se2new50)


stargazer(
  second_stagenew50,
  se = list(sqrt(diag(cluster_senew50))),
  type = "text", omit='factor',
  title = "Second-Stage Regression with Clustered SE at District Level"
)

stargazer(
  LBWIV50, VLBWIV50,
  se = list(sqrt(diag(cluster_se1new50)), sqrt(diag(cluster_se2new50))),  digits=4,
  type = "text",
  title = "50 REGION RESULTS",
  omit = "factor",  
  star.cutoffs = c(0.1, 0.05, 0.01)  
)




```

#60 

```{r}

first_stagenew60 <- lm(
  tri_cumulative ~ avg_north_share_cumulative:factor(regionnew) +
                   avg_east_share_cumulative:factor(regionnew) + 
                   avg_south_share_cumulative:factor(regionnew) +
                   avg_temperature_cumulative + avg_wind_speed_cumulative +religion+minoritycastetribe+cooking+female+urban+bmi+wealth_index+anemia + factor(regionnew):factor(MOB) +factor(YOB)+bord+age_birth,
  data = FinalDataset
)



FinalDataset$tri_cumulative_hatnew <- predict(first_stagenew60)


FinalDataset$first_stage_residuals60 <- residuals(first_stagenew60)


second_stagenew <- lm(
    brthwt ~ tri_cumulative_hatnew + avg_temperature_cumulative + avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + factor(regionnew):factor(MOB) + factor(YOB) + bord +age_birth,
  data = FinalDataset
)


cluster_senew <- vcovCL(second_stagenew, cluster = ~district_matched, type='HC1')

summary_clusterednew <- coeftest(second_stagenew, vcov. = cluster_senew)




LBWIV60<- lm(
  LBW ~ tri_cumulative_hatnew + avg_temperature_cumulative +
          avg_wind_speed_cumulative + minoritycastetribe + religion + cooking + female +
          urban + bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset)



VLBWIV60 <- lm(
  VLBW ~ tri_cumulative_hatnew + avg_temperature_cumulative  +
          avg_wind_speed_cumulative + minoritycastetribe + religion + cooking + female +
          urban + bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)





cluster_se1new <- vcovCL(LBWIV60, cluster = ~district_matched, type='HC1')
summary_clustered1new <- coeftest(LBWIV60, vcov. = cluster_se1new)

cluster_se2new <- vcovCL(VLBWIV60, cluster = ~district_matched, type = "HC1")
summary_clustered2new<- coeftest(VLBWIV60, vcov. = cluster_se2new)




stargazer(second_stagenew,
  LBWIV60, VLBWIV60,
  se = list(sqrt(diag(cluster_senew)), sqrt(diag(cluster_se1new)), sqrt(diag(cluster_se2new))),  digits=4,
  type = "text",
  title = "REGION 60 RESULTS",
  omit = "factor",  
  star.cutoffs = c(0.1, 0.05, 0.01)  
)
```
#Creating Monotonicity Figures

```{r}
#FOR BW

#extract Coefficients + Clustered Standard Errors
extract_coefs <- function(summary_model, var_name, regions) {
  est <- summary_model[var_name, 1]  # Extract Coefficient
  se <- summary_model[var_name, 2]   # Extract Clustered Standard Error
  return(data.frame(Regions = regions, Estimate = est, SE = se))
}

# Create a dataframe with all models
coef_data <- bind_rows(
  extract_coefs(summary_clustered, "tri_cumulative_hat", 30),
  extract_coefs(summary_clusterednew, "tri_cumulative_hatnew", 60),
  extract_coefs(summary_clusterednew50, "tri_cumulative_hatnew50", 50),
  extract_coefs(summary_clusterednew40, "tri_cumulative_hatnew40", 40),
)

# Create the Coefficient Plot
ggplot(coef_data, aes(x = factor(Regions), y = Estimate, color = factor(Regions))) +
  geom_point(size = 3) +  # Plot coefficients
  geom_errorbar(aes(ymin = Estimate - 1.96 * SE, ymax = Estimate + 1.96 * SE), width = 0.2, size=1.3) +  # 95% CI
  geom_hline(yintercept = 0, linetype = "dashed", color = "red",size=1.5) +  # Reference Line at 0
  scale_color_manual(values = c("blue", "red", "green", "orange", "pink")) +  # Custom colors
  labs(
    title = "Robustness: Instrumental Variation Over Differential Number of Regions",
    x = "Number of Geographical Regions For Instruments",
    y = "Coefficient Estimate",
    color = "Regions"
  ) +
  theme_minimal() +  # Clean theme
  theme(legend.position = "bottom")





# FOR LBW

# Create a dataframe with only 30, 40, 50  and 60 region models
coef_data <- bind_rows(
  extract_coefs(summary_clustered1, "tri_cumulative_hat", 30),
  extract_coefs(summary_clustered1new50, "tri_cumulative_hatnew50", 50),
  extract_coefs(summary_clustered1new40, "tri_cumulative_hatnew40", 40),
  extract_coefs(summary_clustered1new, "tri_cumulative_hatnew", 60)
)

#creating the Coefficient Plot
ggplot(coef_data, aes(x = factor(Regions), y = Estimate, color = factor(Regions))) +
  geom_point(size = 3) +  # Plot coefficients
  geom_errorbar(aes(ymin = Estimate - 1.96 * SE, ymax = Estimate + 1.96 * SE), width = 0.2, size = 1.3) +  # 95% CI
  geom_hline(yintercept = 0, linetype = "dashed", color = "red", size = 1.5) +  # Reference Line at 0
  scale_color_manual(values = c("blue", "red", "green", "orange", "pink")) +  # Custom colors for 30, 40, 50
  labs(
    title = "Robustness: Instrumental Variation Over Differential Number of Regions",
    x = "Number of Geographical Regions",
    y = "Coefficient Estimate",
    color = "Regions"
  ) +
  theme_minimal() + 
  theme(legend.position = "bottom")

#FOR VLBW


coef_data <- bind_rows(
  extract_coefs(summary_clustered2, "tri_cumulative_hat", 30),
  extract_coefs(summary_clustered2new50, "tri_cumulative_hatnew50", 50),
  extract_coefs(summary_clustered2new40, "tri_cumulative_hatnew40", 40),
  extract_coefs(summary_clustered2new, "tri_cumulative_hatnew", 60)
)

ggplot(coef_data, aes(x = factor(Regions), y = Estimate, color = factor(Regions))) +
  geom_point(size = 3) +  # Plot coefficients
  geom_errorbar(aes(ymin = Estimate - 1.96 * SE, ymax = Estimate + 1.96 * SE), width = 0.2, size = 1.3) +  # 95% CI
  geom_hline(yintercept = 0, linetype = "dashed", color = "red", size = 1.5) +  # Reference Line at 0
  scale_color_manual(values = c("blue", "red", "green", "orange", "pink")) +  # Custom colors for 30, 40, 50
  labs(
    title = "Robustness: Instrumental Variation Over Differential Number of Regions",
    x = "Number of Geographical Regions",
    y = "Coefficient Estimate",
    color = "Regions"
  ) +
  theme_minimal() + 
  theme(legend.position = "bottom")

```



#Alternative Clustering (Deterministic Hierarchial) 30 Regions based on Hierarchical Clustering
```{r}
first_stagehi <- lm(
  tri_cumulative ~ avg_north_share_cumulative:factor(region30hi) +
                   avg_east_share_cumulative:factor(region30hi) +    avg_south_share_cumulative:factor(region30hi) + 
                   avg_temperature_cumulative + avg_wind_speed_cumulative +religion+minoritycastetribe+cooking+female+urban+bmi+wealth_index+anemia + factor(region30hi):factor(MOB) + factor(YOB)+bord+age_birth,
  data = FinalDataset
)

instr_varshi <- grep("avg_north_share_cumulative|avg_east_share_cumulative|avg_south_share_cumulative", 
                   names(coef(first_stagehi)), value = TRUE)



vcov_clusteredhi <- vcovCL(first_stagehi, cluster = ~district_matched, type = "HC1")


f_test_clusteredhi <- linearHypothesis(first_stagehi, instr_varshi, vcov = vcov_clusteredhi)


print(f_test_clusteredhi)

f_stat_clusteredhi <- f_test_clusteredhi$F[2]
print(f_stat_clusteredhi)



FinalDataset$tri_cumulative_hathi <- predict(first_stagehi)

second_stagehi <- lm(
    brthwt ~ tri_cumulative_hathi + avg_temperature_cumulative  + avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + factor(region30hi):factor(MOB) + factor(YOB) + bord +age_birth ,
  data = FinalDataset
)

cluster_sehi <- vcovCL(second_stagehi, cluster = ~district_matched, type='HC1')

summary_clusteredhi <- coeftest(second_stagehi, vcov. = cluster_sehi)


second_stagehiLBW <- lm(
    LBW ~ tri_cumulative_hathi + avg_temperature_cumulative +  avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + factor(region30hi) :factor(MOB) + factor(YOB) + bord +age_birth ,
  data = FinalDataset
)


cluster_sehiLBW <- vcovCL(second_stagehiLBW, cluster = ~district_matched, type='HC1')


summary_clusteredhiLBW <- coeftest(second_stagehiLBW, vcov. = cluster_sehiLBW)

second_stagehiVLBW <- lm(
    VLBW ~ tri_cumulative_hathi + avg_temperature_cumulative +  avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + factor(region30hi) :factor(MOB) + factor(YOB) + bord +age_birth ,
  data = FinalDataset
)


cluster_sehiVLBW <- vcovCL(second_stagehiVLBW, cluster = ~district_matched, type='HC1')


summary_clusteredhiVLBW <- coeftest(second_stagehiVLBW, vcov. = cluster_sehiVLBW)




stargazer(
  second_stagehi,second_stagehiLBW, second_stagehiVLBW,
  se = list(sqrt(diag(cluster_sehi)),sqrt(diag(cluster_sehiLBW)), sqrt(diag(cluster_sehiVLBW))),
  type = "text", omit='factor',
  title = "IV results from Hierarhcial Clustering (30 Regions)", keep = c('tri_cumulative_hathi'),
  digits = 4
)

```


#Most predictive Wind Direction Per region and re-running first stage and second stages

#most polluting direction
```{r}

model <-  lm(
  tri_cumulative ~ avg_north_share_cumulative:factor(region) +
                   avg_east_share_cumulative:factor(region)  +   avg_south_share_cumulative:factor(region)  + 
                   avg_temperature_cumulative  + avg_wind_speed_cumulative +religion+minoritycastetribe+cooking+female+urban+bmi+wealth_index+ anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)                    
                    
                    
# Extract coefficients
coefs <- summary(model)$coefficients
coef_names <- rownames(coefs)

# Identify wind-direction × region interaction terms to ensure strongest is selected
interaction_rows <- coef_names[
  str_detect(coef_names, "avg_(north|east|south)_share_cumulative.*factor\\(region\\)|factor\\(region\\).*avg_(north|east|south)_share_cumulative")
]

# Build data frame with direction, region, and coefficient
wind_coefs <- data.frame(
  term = interaction_rows,
  coef = coefs[interaction_rows, "Estimate"]
)

# Extract direction and region from term
wind_coefs$direction <- str_extract(wind_coefs$term, "north|east|south")
wind_coefs$region <- as.numeric(str_extract(wind_coefs$term, "(?<=factor\\(region\\))\\d+"))

# Get direction with largest absolute coefficient per region
best_direction_by_region <- wind_coefs %>%
  group_by(region) %>%
  slice_max(order_by = abs(coef), n = 1)

# View results
print(best_direction_by_region)




```

```{r}
best_direction_by_region <- best_direction_by_region %>% select(-term)

# Ensure region columns are both character (to avoid matching issues)
FinalDataset$region <- as.character(FinalDataset$region)
best_direction_by_region$region <- as.character(best_direction_by_region$region)

# Merge direction info into FinalDataset
FinalDataset <- FinalDataset %>%
  left_join(best_direction_by_region, by = "region")  # Adds `direction` column

# Create windmost column based on the direction
FinalDataset$windmost <- NA

# For each direction, assign the corresponding wind share
for (dir in c("north", "east", "south")) {
  colname <- paste0("avg_", dir, "_share_cumulative")
  FinalDataset$windmost[FinalDataset$direction == dir] <- 
    FinalDataset[[colname]][FinalDataset$direction == dir]
}

```


```{r}
first_stagewindmost <- lm(
  tri_cumulative ~ windmost:factor(region) +
                   avg_temperature_cumulative + avg_wind_speed_cumulative +
                   religion + minoritycastetribe + cooking + female + urban + bmi +
                   wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) +
                   bord + age_birth,
  data = FinalDataset
)



instr_varswindmost <- grep("windmost", 
                   names(coef(first_stagewindmost)), value = TRUE)

vcov_clusteredwindmost <- vcovCL(first_stagewindmost, cluster = ~district_matched, type = "HC1")


f_test_clusteredwindmost <- linearHypothesis(first_stagewindmost, instr_varswindmost, vcov = vcov_clusteredwindmost)

print(f_test_clusteredwindmost)


f_stat_clusteredwindmost <- f_test_clusteredwindmost$F[2]
print(f_stat_clusteredwindmost)





FinalDataset$tri_cumulative_hatwindmost <- predict(first_stagewindmost)

second_stagewindmostBW <- lm(
    brthwt ~ tri_cumulative_hatwindmost  + avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + factor(region):factor(MOB) + factor(YOB) + bord +age_birth ,
  data = FinalDataset
)

second_stagewindmostLBW <- lm(
    LBW ~ tri_cumulative_hatwindmost   + avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + factor(region):factor(MOB) + factor(YOB) + bord +age_birth ,
  data = FinalDataset
)

second_stagewindmostVLBW <- lm(
   VLBW ~ tri_cumulative_hatwindmost   + avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + factor(region):factor(MOB) + factor(YOB) + bord +age_birth ,
  data = FinalDataset
)




cluster_se_bw <- vcovCL(second_stagewindmostBW, cluster = ~district_matched, type='HC1')
summary_clusteredwindmostBW <- coeftest(second_stagewindmostBW, vcov. = cluster_se_bw)

cluster_se_lbw <- vcovCL(second_stagewindmostLBW,
                         cluster = ~ district_matched,
                         type = "HC1")

summary_clusteredwindmostLBW <- coeftest(second_stagewindmostLBW,
                                         vcov. = cluster_se_lbw)

cluster_se_vlbw <- vcovCL(second_stagewindmostVLBW,
                          cluster = ~ district_matched,
                          type = "HC1")
summary_clusteredwindmostVLBW <- coeftest(second_stagewindmostVLBW,
                                          vcov. = cluster_se_vlbw)


stargazer(
  second_stagewindmostBW, second_stagewindmostLBW, second_stagewindmostVLBW,
  se = list(
  sqrt(diag(cluster_se_bw)),
  sqrt(diag(cluster_se_lbw)), sqrt(diag(cluster_se_vlbw))
),
  type = "text",
  title = "Second-Stage IV Results with Clustered Standard Errors",
  column.labels = c("Birth Weight", "LBW",'VLBW'),
  dep.var.labels.include = FALSE,
  keep = c("tri_cumulative_hatwindmost"),
  covariate.labels = c("Predicted PM2.5 (IV)"),
  add.lines = list(c('First stage F-statistic', f_stat_clusteredwindmost,f_stat_clusteredwindmost,f_stat_clusteredwindmost)),
  omit.stat = c("f", "ser"),
  no.space = TRUE,
  digits = 4
)

```
# Card Only Sample Robustness
```{r}

FinalDatasetFilteredCard <- FinalDataset %>% filter(card_recall==1)

first_stageCARD <- lm(
  tri_cumulative ~ avg_north_share_cumulative:factor(region) +
                   avg_east_share_cumulative:factor(region) +    avg_south_share_cumulative:factor(region) + 
                   avg_temperature_cumulative  + avg_wind_speed_cumulative +religion+minoritycastetribe+cooking+female+urban+bmi+wealth_index+anemia + factor(region):factor(MOB) + factor(YOB)+bord+age_birth,
  data = FinalDatasetFilteredCard
)


FinalDatasetFilteredCard$tri_cumulative_hatCARD <- predict(first_stageCARD)

second_stageCARD <- lm(
    brthwt ~ tri_cumulative_hatCARD + avg_temperature_cumulative + avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + factor(region):factor(MOB) + factor(YOB) + bord +age_birth ,
  data = FinalDatasetFilteredCard
)

cluster_seCARD <- vcovCL(second_stageCARD, cluster = ~district_matched, type='HC1')


summary_clusteredCARD <- coeftest(second_stageCARD, vcov. = cluster_seCARD)


second_stageCARDLBW <- lm(
    LBW ~ tri_cumulative_hatCARD + avg_temperature_cumulative +  avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + factor(region):factor(MOB) + factor(YOB) + bord +age_birth ,
  data = FinalDatasetFilteredCard
)


cluster_seCARDLBW <- vcovCL(second_stageCARDLBW, cluster = ~district_matched, type='HC1')


summary_clusteredCARDLBW <- coeftest(second_stageCARDLBW, vcov. = cluster_seCARDLBW)



second_stageCARDVLBW <- lm(
    VLBW ~ tri_cumulative_hatCARD + avg_temperature_cumulative +  avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + factor(region):factor(MOB) + factor(YOB) + bord +age_birth ,
  data = FinalDatasetFilteredCard
)

cluster_seCARDVLBW <- vcovCL(second_stageCARDVLBW, cluster = ~district_matched, type='HC1')


summary_clusteredCARDVLBW <- coeftest(second_stageCARDVLBW, vcov. = cluster_seCARDVLBW)


instr_varsCARD <- grep("avg_north_share_cumulative|avg_east_share_cumulative|avg_south_share_cumulative", 
                   names(coef(first_stageCARD)), value = TRUE)




vcov_clusteredCARD <- vcovCL(first_stageCARD, cluster = ~district_matched, type = "HC1")

f_test_clusteredCARD <- linearHypothesis(first_stageCARD, instr_varsCARD, vcov = vcov_clusteredCARD)


print(f_test_clusteredCARD)


f_stat_clusteredCARD <- f_test_clusteredCARD$F[2]
print(f_stat_clusteredCARD)



stargazer(
  second_stageCARD,second_stageCARDLBW,second_stageCARDVLBW,
  se = list(sqrt(diag(cluster_seCARD)),sqrt(diag(cluster_seCARDLBW)), sqrt(diag(cluster_seCARDVLBW))),
  type = "text", omit='factor',
  title = "IV estimates: Card Only Sample", keep = c('tri_cumulative_hatCARD'),
  digits = 4
)


mean(FinalDatasetFilteredCard$LBW)

mean(FinalDatasetFilteredCard$brthwt)

mean(FinalDatasetFilteredCard$VLBW)
```

# Alternative Clustering of SEs

```{r}
cluster_sestate <- vcovCL(second_stage, cluster = ~state_matched)
summary_clusteredstate <- coeftest(second_stage, vcov. = cluster_sestate)

cluster_seregion <- vcovCL(second_stage, cluster = ~region)
summary_clusteredregion <- coeftest(second_stage, vcov. = cluster_seregion)

cluster_sestateLBW <- vcovCL(LBWbaselineIV, cluster = ~state_matched)
summary_clusteredstateLBW <- coeftest(LBWbaselineIV, vcov. = cluster_sestateLBW)

cluster_seregionLBW <- vcovCL(LBWbaselineIV, cluster = ~region)
summary_clusteredregionLBW<- coeftest(LBWbaselineIV, vcov. = cluster_seregionLBW)

cluster_sestateVLBW <- vcovCL(VLBWbaselineIV, cluster = ~state_matched)
summary_clusteredstateVLBW <- coeftest(VLBWbaselineIV, vcov. = cluster_sestateVLBW)

cluster_seregionVLBW<- vcovCL(VLBWbaselineIV, cluster = ~region)
summary_clusteredregionVLBW <- coeftest(VLBWbaselineIV, vcov. = cluster_seregionVLBW)


```

```{r}

# Function to extract only tri_cumulative_hat coefficient
extract_tri_hat <- function(summary_model, model_name) {
  tidy_model <- tidy(summary_model)  # Convert to dataframe
  tri_row <- tidy_model %>% filter(term == "tri_cumulative_hat")  # Select only tri_cumulative_hat
  data.frame(
    Model = model_name,
    Estimate = tri_row$estimate,
    SE = tri_row$std.error
  )
}

coef_data <- bind_rows(
  extract_tri_hat(summary_clustered, "District"),
  extract_tri_hat(summary_clusteredstate, "State"),
  extract_tri_hat(summary_clusteredregion, "Region")
)


#baseline BW clustering district, region and state
plot_bw <- ggplot(coef_data, aes(x = Model, y = Estimate, color = Model)) +
  geom_point(size = 4) +  # Coefficients as points
  geom_errorbar(aes(ymin = Estimate - 1.96 * SE, ymax = Estimate + 1.96 * SE), width = 0.2, size = 1.3) +  # 95% CI
  geom_hline(yintercept = 0, linetype = "dashed", color = "red", size = 1.5) +  # Reference Line at 0
  labs(
    title = "Birth Weight : Coefficient Estimates Baseline with Alternative Clustering of SE's",
    x = "SE Clustering Choice",
    y = "Coefficient Estimate",
    color = "level of clustering"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom")

plot_bw

#LBW
coef_data_lbw <- bind_rows(
  extract_tri_hat(summary_clustered1, "District"),
  extract_tri_hat(summary_clusteredstateLBW, "State"),
  extract_tri_hat(summary_clusteredregionLBW, "Region")
)


plot_lbw <- ggplot(coef_data_lbw, aes(x = Model, y = Estimate, color = Model)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = Estimate - 1.96 * SE, ymax = Estimate + 1.96 * SE), width = 0.2, size = 1.3) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red", size = 1.5) +
  labs(
    title = "LBW : Coefficient Estimates Baseline with Alternative Clustering of SE's",
    x = "SE Clustering Level",
    y = "Coefficient Estimate",
    color = "level of clustering"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom")

# Show the plot LBW
plot_lbw



# VLBW
coef_data_vlbw <- bind_rows(
  extract_tri_hat(summary_clustered2, "District"),
  extract_tri_hat(summary_clusteredstateVLBW, "State"),
  extract_tri_hat(summary_clusteredregionVLBW, "Region")
)

# Plotting
plot_vlbw <- ggplot(coef_data_vlbw, aes(x = Model, y = Estimate, color = Model)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = Estimate - 1.96 * SE, ymax = Estimate + 1.96 * SE), width = 0.2, size = 1.3) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red", size = 1.5) +
  labs(
    title = "VLBW : Coefficient Estimates Baseline with Alternative Clustering of SE's",
    x = "SE Clustering Level",
    y = "Coefficient Estimate",
    color = "level of clustering"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom")

plot_vlbw

```
#Iterative Robustness dropping states/UTs one by one
```{r}
results_list_iterBW <- list()

for (state_id in 1:36) {
  cat("Dropping state:", state_id, "\n")
  
  # Subset the data excluding one state
  temp_data_iterBW <- FinalDataset %>% filter(state_matched != state_id)

  # First-stage regression
  first_stage_iterBW <- lm(
    tri_cumulative ~ avg_north_share_cumulative:factor(region) +
                     avg_east_share_cumulative:factor(region) +
                     avg_south_share_cumulative:factor(region) +
                     avg_temperature_cumulative + avg_wind_speed_cumulative +
                     religion + minoritycastetribe + cooking + female + urban +
                     bmi + wealth_index + anemia +
                     factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
    data = temp_data_iterBW
  )

  # Identify instrument terms
  instr_vars_iterBW <- grep("avg_(north|east|south)_share_cumulative", names(coef(first_stage_iterBW)), value = TRUE)
  
  # Wald F-test for instruments
  f_test_iterBW <- linearHypothesis(first_stage_iterBW, instr_vars_iterBW, vcov = vcovHC(first_stage_iterBW, type = "HC0"))
  f_stat_iterBW <- f_test_iterBW$F[2]

  # Predicted values for 2SLS
  temp_data_iterBW$tri_cumulative_hat <- predict(first_stage_iterBW, newdata = temp_data_iterBW)

  # Second-stage regression
  second_stage_iterBW <- lm(
    brthwt ~ tri_cumulative_hat + avg_temperature_cumulative +
    avg_wind_speed_cumulative + minoritycastetribe + religion + cooking +
    female + urban + bmi + wealth_index + anemia +
    factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
    data = temp_data_iterBW
  )

  # Clustered SE at district level
  cluster_se_iterBW <- vcovCL(second_stage_iterBW, cluster = ~code, type = 'HC1')
  clustered_summary_iterBW <- coeftest(second_stage_iterBW, vcov. = cluster_se_iterBW)

  # Save output to list
  results_list_iterBW[[paste0("drop_state_", state_id)]] <- list(
    f_stat = f_stat_iterBW,
    coef = clustered_summary_iterBW
  )
}

# Example output display
print(results_list_iterBW[["drop_state_2"]])


# Extract values from results_list_iterBW
states_iterBW <- 1:36
tri_coefs_iterBW <- sapply(results_list_iterBW, function(x) x$coef["tri_cumulative_hat", 1])
tri_se_iterBW    <- sapply(results_list_iterBW, function(x) x$coef["tri_cumulative_hat", 2])

# Calculate 95% confidence intervals
tri_ci_lower_iterBW <- tri_coefs_iterBW - 1.96 * tri_se_iterBW
tri_ci_upper_iterBW <- tri_coefs_iterBW + 1.96 * tri_se_iterBW

# Create dataframe
df_coef_iterBW <- data.frame(
  State = factor(states_iterBW, levels = states_iterBW),
  Coef = tri_coefs_iterBW,
  Lower = tri_ci_lower_iterBW,
  Upper = tri_ci_upper_iterBW
)

# Assign a unique color per state
df_coef_iterBW$ColorGroup <- as.factor(df_coef_iterBW$State)

# Use ggplot with flipped coordinates and add horizontal line at y = 0
ggplot(df_coef_iterBW, aes(y = Coef, x = State, color = ColorGroup)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0.3, size = 1) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Horizontal line at 0
  scale_color_viridis_d(option = "inferno") +
  labs(
    #title = "Impact of PM2.5 on Birth Weight (with 95% CI)",
    #subtitle = "Iteratively Dropping One State/UT at a Time",
    x = "Dropped State/UT Code (From DHS Records)",
    y = "Coefficient"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1, size = 10),
    axis.text.y = element_text(size = 12),
    panel.grid.major.x = element_blank()
  )


```
#LBW Iterative dropping
```{r}
results_list_iterLBW <- list()

for (state_id in 1:36) {
  cat("Dropping state:", state_id, "\n")
  

  temp_data_iterLBW <- FinalDataset %>% filter(state_matched != state_id)


  first_stage_iterLBW <- lm(
    tri_cumulative ~ avg_north_share_cumulative:factor(region) +
                     avg_east_share_cumulative:factor(region) +
                     avg_south_share_cumulative:factor(region) +
                     avg_temperature_cumulative + avg_wind_speed_cumulative +
                     religion + minoritycastetribe + cooking + female + urban +
                     bmi + wealth_index + anemia +
                     factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
    data = temp_data_iterLBW
  )


  instr_vars_iterLBW <- grep("avg_(north|east|south)_share_cumulative", names(coef(first_stage_iterLBW)), value = TRUE)
  
 
  f_test_iterLBW <- linearHypothesis(first_stage_iterLBW, instr_vars_iterLBW, vcov = vcovHC(first_stage_iterLBW, type = "HC0"))
  f_stat_iterLBW <- f_test_iterLBW$F[2]

  temp_data_iterLBW$tri_cumulative_hat <- predict(first_stage_iterLBW, newdata = temp_data_iterLBW)

 
  second_stage_iterLBW <- lm(
    LBW ~ tri_cumulative_hat + avg_temperature_cumulative +
    avg_wind_speed_cumulative + minoritycastetribe + religion + cooking +
    female + urban + bmi + wealth_index + anemia +
    factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
    data = temp_data_iterLBW
  )


  cluster_se_iterLBW <- vcovCL(second_stage_iterLBW, cluster = ~code, type = 'HC1')
  clustered_summary_iterLBW <- coeftest(second_stage_iterLBW, vcov. = cluster_se_iterLBW)


  results_list_iterLBW[[paste0("drop_state_", state_id)]] <- list(
    f_stat = f_stat_iterLBW,
    coef = clustered_summary_iterLBW
  )
}





states_iterLBW <- 1:36
tri_coefs_iterLBW <- sapply(results_list_iterLBW, function(x) x$coef["tri_cumulative_hat", 1])
tri_se_iterLBW    <- sapply(results_list_iterLBW, function(x) x$coef["tri_cumulative_hat", 2])

tri_ci_lower_iterLBW <- tri_coefs_iterLBW - 1.96 * tri_se_iterLBW
tri_ci_upper_iterLBW <- tri_coefs_iterLBW + 1.96 * tri_se_iterLBW


df_coef_iterLBW <- data.frame(
  State = factor(states_iterLBW, levels = states_iterLBW),
  Coef = tri_coefs_iterLBW,
  Lower = tri_ci_lower_iterLBW,
  Upper = tri_ci_upper_iterLBW
)


df_coef_iterLBW$ColorGroup <- as.factor(df_coef_iterLBW$State)


ggplot(df_coef_iterLBW, aes(y = Coef, x = State, color = ColorGroup)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0.3, size = 1) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Horizontal line at 0
  scale_color_viridis_d(option = "inferno") +
  labs(
    #title = "Impact of PM2.5 on Birth Weight (with 95% CI)",
    #subtitle = "Iteratively Dropping One State/UT at a Time",
    x = "Dropped State/UT Code (From DHS Records)",
    y = "Coefficient"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1, size = 10),
    axis.text.y = element_text(size = 12),
    panel.grid.major.x = element_blank()
  )


```

#Above Average Size Robustness Check
```{r}

second_stageabove <- lm(
   above_averagesize  ~ tri_cumulative_hat + avg_temperature_cumulative  + avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth ,
  data = FinalDataset
)

cluster_se_size <- vcovCL(second_stageabove, cluster = ~district_matched, type='HC1' )
sesize <- list(sqrt(diag(cluster_se_size)))



meanbelow <- mean(FinalDataset$below_averagesize,na.rm=TRUE)
meanabove <- 1-meanbelow

stargazer(second_stageabove, type='text',  se=sesize, omit='factor',keep=c('tri_cumulative_hat'), add.lines = list(c('Mean of Dependent Variable', meanabove), c('First stage F-statistic', f_stat_clustered)),digits=4)
```
```{r}
FinalDataset <- FinalDataset %>%
  mutate(
    #Trimester 3
    northsharetri3 = (North_share1 + North_share2 + North_share3) / 3,
    southsharetri3 = (South_share1 + South_share2 + South_share3) / 3,
    eastsharetri3  = (East_share1 + East_share2 + East_share3) / 3,
    windtri3       = (avg_wind_speed1 + avg_wind_speed2 + avg_wind_speed3) / 3,
    temptri3       = (avg_temperature1 + avg_temperature2 + avg_temperature3) / 3,
    pmtri3         = (pm1 + pm2 + pm3) / 3,
    
    
    
    # Trimester 2
    northsharetri2 = (North_share4 + North_share5 + North_share6) / 3,
    southsharetri2 = (South_share4 + South_share5 + South_share6) / 3,
    eastsharetri2  = (East_share4 + East_share5 + East_share6) / 3,
    windtri2       = (avg_wind_speed4 + avg_wind_speed5 + avg_wind_speed6) / 3,
    temptri2       = (avg_temperature4 + avg_temperature5 + avg_temperature6) / 3,
    pmtri2         = (pm4 + pm5 + pm6) / 3,

    # Trimester 1
    northsharetri1 = (North_share7 + North_share8 + North_share9) / 3,
    southsharetri1 = (South_share7 + South_share8 + South_share9) / 3,
    eastsharetri1  = (East_share7 + East_share8 + East_share9) / 3,
    windtri1       = (avg_wind_speed7 + avg_wind_speed8 + avg_wind_speed9) / 3,
    temptri1       = (avg_temperature7 + avg_temperature8 + avg_temperature9) / 3,
    pmtri1         = (pm7 + pm8 + pm9) / 3
  )

#TRIMESTER 3
first_stagetri3 <- lm(
  pmtri3 ~ northsharetri3:factor(region) + eastsharetri3:factor(region) + southsharetri3:factor(region) +
    temptri3 + windtri3 + religion + minoritycastetribe + cooking + female + urban +
    bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

FinalDataset$tri_hat3 <- predict(first_stagetri3)
instr_varstri3 <- grep("northsharetri3|eastsharetri3|southsharetri3", names(coef(first_stagetri3)), value = TRUE)
vcov_clusteredtri3 <- vcovCL(first_stagetri3, cluster = ~code, type = "HC1")
f_test_clusteredtri3 <- linearHypothesis(first_stagetri3, instr_varstri3, vcov = vcov_clusteredtri3)
f_stat_clusteredtri3 <- f_test_clusteredtri3$F[2]
print(f_stat_clusteredtri3)

second_stagetri3BW <- lm(
  brthwt ~ tri_hat3 + temptri3 + windtri3 + minoritycastetribe + religion + cooking + female + urban +
    bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

second_stagetri3LBW <- lm(
  LBW ~ tri_hat3 + temptri3 + windtri3 + minoritycastetribe + religion + cooking + female + urban +
    bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

second_stagetri3VLBW <- lm(
  VLBW ~ tri_hat3 + temptri3 + windtri3 + minoritycastetribe + religion + cooking + female + urban +
    bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

se_tri3_bw <- sqrt(diag(vcovCL(second_stagetri3BW, cluster = ~code, type = "HC1")))
se_tri3_lbw <- sqrt(diag(vcovCL(second_stagetri3LBW, cluster = ~code, type = "HC1")))
se_tri3_vlbw <- sqrt(diag(vcovCL(second_stagetri3VLBW, cluster = ~code, type = "HC1")))



#TRIMESTER 2 
first_stagetri2 <- lm(
  pmtri2 ~ northsharetri2:factor(region) + eastsharetri2:factor(region) + southsharetri2:factor(region) +
    temptri2 + windtri2 + religion + minoritycastetribe + cooking + female + urban +
    bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

FinalDataset$tri_hat2 <- predict(first_stagetri2)
instr_varstri2 <- grep("northsharetri2|eastsharetri2|southsharetri2", names(coef(first_stagetri2)), value = TRUE)
vcov_clusteredtri2 <- vcovCL(first_stagetri2, cluster = ~code, type = "HC1")
f_test_clusteredtri2 <- linearHypothesis(first_stagetri2, instr_varstri2, vcov = vcov_clusteredtri2)
f_stat_clusteredtri2 <- f_test_clusteredtri2$F[2]
print(f_stat_clusteredtri2)

second_stagetri2BW <- lm(
  brthwt ~ tri_hat2 + temptri2 + windtri2 + minoritycastetribe + religion + cooking + female + urban +
    bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

second_stagetri2LBW <- lm(
  LBW ~ tri_hat2 + temptri2 + windtri2 + minoritycastetribe + religion + cooking + female + urban +
    bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

second_stagetri2VLBW <- lm(
  VLBW ~ tri_hat2 + temptri2 + windtri2 + minoritycastetribe + religion + cooking + female + urban +
    bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

se_tri2_bw <- sqrt(diag(vcovCL(second_stagetri2BW, cluster = ~code, type = "HC1")))
se_tri2_lbw <- sqrt(diag(vcovCL(second_stagetri2LBW, cluster = ~code, type = "HC1")))
se_tri2_vlbw <- sqrt(diag(vcovCL(second_stagetri2VLBW, cluster = ~code, type = "HC1")))

# TRIMESTER 1
first_stagetri1 <- lm(
  pmtri1 ~ northsharetri1:factor(region) + eastsharetri1:factor(region) + southsharetri1:factor(region) +
    temptri1 + windtri1 + religion + minoritycastetribe + cooking + female + urban +
    bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

FinalDataset$tri_hat1 <- predict(first_stagetri1)
instr_varstri1 <- grep("northsharetri1|eastsharetri1|southsharetri1", names(coef(first_stagetri1)), value = TRUE)
vcov_clusteredtri1 <- vcovCL(first_stagetri1, cluster = ~code, type = "HC1")
f_test_clusteredtri1 <- linearHypothesis(first_stagetri1, instr_varstri1, vcov = vcov_clusteredtri1)
f_stat_clusteredtri1 <- f_test_clusteredtri1$F[2]
print(f_stat_clusteredtri1)

second_stagetri1BW <- lm(
  brthwt ~ tri_hat1 + temptri1 + windtri1 + minoritycastetribe + religion + cooking + female + urban +
    bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

second_stagetri1LBW <- lm(
  LBW ~ tri_hat1 + temptri1 + windtri1 + minoritycastetribe + religion + cooking + female + urban +
    bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

second_stagetri1VLBW <- lm(
  VLBW ~ tri_hat1 + temptri1 + windtri1 + minoritycastetribe + religion + cooking + female + urban +
    bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

se_tri1_bw <- sqrt(diag(vcovCL(second_stagetri1BW, cluster = ~code, type = "HC1")))
se_tri1_lbw <- sqrt(diag(vcovCL(second_stagetri1LBW, cluster = ~code, type = "HC1")))
se_tri1_vlbw <- sqrt(diag(vcovCL(second_stagetri1VLBW, cluster = ~code, type = "HC1")))


# Trimester 3 table
stargazer(
  second_stagetri3BW, second_stagetri3LBW, second_stagetri3VLBW,
  type = "text",
  se = list(se_tri3_bw, se_tri3_lbw, se_tri3_vlbw), digits=5,
  keep = c('tri_hat3'))


# Trimester 2 table
stargazer(
  second_stagetri2BW, second_stagetri2LBW, second_stagetri2VLBW,
  type = "text", digits=5,
  se = list(se_tri2_bw, se_tri2_lbw, se_tri2_vlbw),
  keep = c('tri_hat2'))

# Trimester 1 table
stargazer(
  second_stagetri1BW, second_stagetri1LBW, second_stagetri1VLBW,
  type = "text", digits=5,
  se = list(se_tri1_bw, se_tri1_lbw, se_tri1_vlbw),
  keep = c('tri_hat1'),
  omit.stat = c("f", "ser")
)

```
#Outliers Filtered (bw 1st and 99th percentile)
```{r}

brthwt_bounds <- quantile(FinalDataset$brthwt, probs = c(0.01, 0.99), na.rm = TRUE)


FinalDatasetFilteredOUTLIERS <- FinalDataset %>%
  filter(brthwt > brthwt_bounds[1], brthwt < brthwt_bounds[2])


first_stageOUTLIERS <- lm(
  tri_cumulative ~ avg_north_share_cumulative:factor(region) +
                   avg_east_share_cumulative:factor(region) +    avg_south_share_cumulative:factor(region) + 
                   avg_temperature_cumulative + avg_wind_speed_cumulative +religion+minoritycastetribe+cooking+female+urban+bmi+wealth_index+anemia + factor(region):factor(MOB) + factor(YOB)+bord+age_birth,
  data = FinalDatasetFilteredOUTLIERS
)




FinalDatasetFilteredOUTLIERS$tri_cumulative_hatOUTLIERS <- predict(first_stageOUTLIERS)

second_stageOUTLIERS <- lm(
    brthwt ~ tri_cumulative_hatOUTLIERS + avg_temperature_cumulative+ avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + factor(region):factor(MOB) + factor(YOB) + bord +age_birth ,
  data = FinalDatasetFilteredOUTLIERS
)

cluster_seOUTLIERS <- vcovCL(second_stageOUTLIERS, cluster = ~code, type='HC1')

summary_clusteredOUTLIERS <- coeftest(second_stageOUTLIERS, vcov. = cluster_seOUTLIERS)


second_stageOUTLIERSLBW <- lm(
    LBW ~ tri_cumulative_hatOUTLIERS + avg_temperature_cumulative  + avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + factor(region):factor(MOB) + factor(YOB) + bord +age_birth ,
  data = FinalDatasetFilteredOUTLIERS
)


cluster_seOUTLIERSLBW <- vcovCL(second_stageOUTLIERSLBW, cluster = ~code, type='HC1')


summary_clusteredOUTLIERSLBW <- coeftest(second_stageOUTLIERSLBW, vcov. = cluster_seOUTLIERSLBW)


stargazer(
  second_stageOUTLIERS,second_stageOUTLIERSLBW,
  se = list(sqrt(diag(cluster_seOUTLIERS)),sqrt(diag(cluster_seOUTLIERSLBW))),
  type = "text", omit='factor',
  title = "Outliers Filtered: BW between 1st and 99th percentile", keep = c('tri_cumulative_hatOUTLIERS','avg_temperature_cumulative'),
  digits = 4
)

instr_varsOUTLIERS <- grep("avg_north_share_cumulative|avg_east_share_cumulative|avg_south_share_cumulative", 
                   names(coef(first_stageOUTLIERS)), value = TRUE)





vcov_clusteredOUTLIERS <- vcovCL(first_stageOUTLIERS, cluster = ~code, type = "HC1")


f_test_clusteredOUTLIERS <- linearHypothesis(first_stageOUTLIERS, instr_varsOUTLIERS, vcov = vcov_clusteredOUTLIERS)


print(f_test_clusteredOUTLIERS)


f_stat_clusteredOUTLIERS <- f_test_clusteredOUTLIERS$F[2]
print(f_stat_clusteredOUTLIERS)

mean(FinalDatasetFilteredOUTLIERS$LBW)

mean(FinalDatasetFilteredOUTLIERS$brthwt)
```

#Outliers bewteen 2.5th and 97.5th percentile or between 1600 and 4000 grams (same)
```{r}

brthwt_bounds <- quantile(FinalDataset$brthwt, probs = c(0.025, 0.975), na.rm = TRUE)


FinalDatasetFilteredOUTLIERS1 <- FinalDataset %>%
  filter(brthwt > brthwt_bounds[1], brthwt < brthwt_bounds[2])


first_stageOUTLIERS1 <- lm(
  tri_cumulative ~ avg_north_share_cumulative:factor(region) +
                   avg_east_share_cumulative:factor(region) +    avg_south_share_cumulative:factor(region) + 
                   avg_temperature_cumulative + avg_wind_speed_cumulative +religion+minoritycastetribe+cooking+female+urban+bmi+wealth_index+anemia + factor(region):factor(MOB) + factor(YOB)+bord+age_birth,
  data = FinalDatasetFilteredOUTLIERS1
)




FinalDatasetFilteredOUTLIERS1$tri_cumulative_hatOUTLIERS1 <- predict(first_stageOUTLIERS1)

second_stageOUTLIERS1 <- lm(
    brthwt ~ tri_cumulative_hatOUTLIERS1 + avg_temperature_cumulative+ avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + factor(region):factor(MOB) + factor(YOB) + bord +age_birth ,
  data = FinalDatasetFilteredOUTLIERS1
)


cluster_seOUTLIERS1 <- vcovCL(second_stageOUTLIERS1, cluster = ~code, type='HC1')


summary_clusteredOUTLIERS1 <- coeftest(second_stageOUTLIERS1, vcov. = cluster_seOUTLIERS1)


second_stageOUTLIERSLBW1 <- lm(
    LBW ~ tri_cumulative_hatOUTLIERS1 + avg_temperature_cumulative  + avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + factor(region):factor(MOB) + factor(YOB) + bord +age_birth ,
  data = FinalDatasetFilteredOUTLIERS1
)


cluster_seOUTLIERSLBW1 <- vcovCL(second_stageOUTLIERSLBW1, cluster = ~code, type='HC1')


summary_clusteredOUTLIERSLBW1 <- coeftest(second_stageOUTLIERSLBW1, vcov. = cluster_seOUTLIERSLBW1)



stargazer(
  second_stageOUTLIERS1,second_stageOUTLIERSLBW1,
  se = list(sqrt(diag(cluster_seOUTLIERS1)),sqrt(diag(cluster_seOUTLIERSLBW1))),
  type = "text", omit='factor',
  title = "Outliers Filtered: BW between 2.5th and 97.5th percentile", keep = c('tri_cumulative_hatOUTLIERS1'),
  digits = 4)


instr_varsOUTLIERS1 <- grep("avg_north_share_cumulative|avg_east_share_cumulative|avg_south_share_cumulative", 
                   names(coef(first_stageOUTLIERS1)), value = TRUE)





vcov_clusteredOUTLIERS1 <- vcovCL(first_stageOUTLIERS1, cluster = ~code, type = "HC1")


f_test_clusteredOUTLIERS1 <- linearHypothesis(first_stageOUTLIERS1, instr_varsOUTLIERS1, vcov = vcov_clusteredOUTLIERS1)

print(f_test_clusteredOUTLIERS1)


f_stat_clusteredOUTLIERS1 <- f_test_clusteredOUTLIERS1$F[2]
print(f_stat_clusteredOUTLIERS1)


mean(FinalDatasetFilteredOUTLIERS1$LBW)

mean(FinalDatasetFilteredOUTLIERS1$brthwt)

```


# Robustness using Van Donkelaar Data
```{r}
FinalDatasetVanDonk <- FinalDataset %>% filter(!is.na(pmvandonk_cumulative))

first_stageVanDonk <- lm(
  pmvandonk_cumulative ~ North_share_cumulative:factor(region) +
                   East_share_cumulative:factor(region)  +   South_share_cumulative:factor(region)  + 
                   temp_cumulative  + windspeed_cumulative + factor(religion_code) + dirty_cookingfuel+sex_child+urban+bmi+factor(wealth_index) + factor(anemic) + factor(region):factor(month_birth) + factor(year_birth) + birthorder + age_birth+ factor(caste),
  data = FinalDatasetVanDonk
)

summary(first_stageVanDonk)


FinalDatasetVanDonk$tri_cumulative_hat <- predict(first_stageVanDonk)


second_stageVanDonkBW <- lm(
  birthweight ~ tri_cumulative_hat  + 
                   temp_cumulative  + windspeed_cumulative + factor(religion_code) + dirty_cookingfuel+sex_child+urban+bmi+factor(wealth_index) + factor(anemic) + factor(region):factor(month_birth) + factor(year_birth) + birthorder + age_birth+ factor(caste),
  data = FinalDatasetVanDonk
)

cluster_seVanDonkBW <- vcovCL(second_stageVanDonkBW, cluster = ~code, type='HC1')

second_stageVanDonkLBW <- lm(
  lbw ~ tri_cumulative_hat  + 
                   temp_cumulative  + windspeed_cumulative + factor(religion_code) + dirty_cookingfuel+sex_child+urban+bmi+factor(wealth_index) + factor(anemic) + factor(region):factor(month_birth) + factor(year_birth) + birthorder + age_birth+ factor(caste),
  data = FinalDatasetVanDonk
)

cluster_seVanDonkLBW <- vcovCL(second_stageVanDonkLBW, cluster = ~code, type='HC1')

second_stageVanDonkVLBW <- lm(
 vlbw ~ tri_cumulative_hat  + 
                   temp_cumulative  + windspeed_cumulative + factor(religion_code) + dirty_cookingfuel+sex_child+urban+bmi+factor(wealth_index) + factor(anemic) + factor(region):factor(month_birth) + factor(year_birth) + birthorder + age_birth+ factor(caste),
  data = FinalDatasetVanDonk
)


cluster_seVanDonkVLBW <- vcovCL(second_stageVanDonkVLBW, cluster = ~code, type='HC1')



stargazer(
  second_stageVanDonkBW, second_stageVanDonkLBW, second_stageVanDonkVLBW,
  se = list(sqrt(diag(cluster_seVanDonkBW)),sqrt(diag(cluster_seVanDonkLBW)),sqrt(diag(cluster_seVanDonkVLBW))),digits=4,
  type = "text", omit='factor',
  title = "Second-Stage Regression with Clustered SE at District Level"
)


instr_varsVanDonk <- grep("North_share_cumulative|East_share_cumulative|South_share_cumulative", 
                   names(coef(first_stageVanDonk)), value = TRUE)

vcov_clusteredVanDonk <- vcovCL(first_stageVanDonk, cluster = ~code, type = "HC1")

f_test_clusteredVanDonk <- linearHypothesis(first_stageVanDonk, instr_varsVanDonk, vcov = vcov_clusteredVanDonk)



f_stat_clusteredVanDonk <- f_test_clusteredVanDonk$F[2]
print(f_stat_clusteredVanDonk)


```

#OLS Using Van Donk Data
```{r}
VanDonkBWOLS <- lm(
  birthweight ~ pmvandonk_cumulative  + 
                   temp_cumulative  + windspeed_cumulative + factor(religion_code) + dirty_cookingfuel+sex_child+urban+bmi+factor(wealth_index) + factor(anemic) + factor(region):factor(month_birth) + factor(year_birth) + birthorder + age_birth+ factor(caste),
  data = FinalDatasetVanDonk
)

cluster_seVanDonkBWOLS <- vcovCL(VanDonkBWOLS, cluster = ~code, type='HC1')

VanDonkLBWOLS <- lm(
  lbw ~ pmvandonk_cumulative  + 
                   temp_cumulative  + windspeed_cumulative + factor(religion_code) + dirty_cookingfuel+sex_child+urban+bmi+factor(wealth_index) + factor(anemic) + factor(region):factor(month_birth) + factor(year_birth) + birthorder + age_birth+ factor(caste),
  data = FinalDatasetVanDonk
)

cluster_seVanDonkLBWOLS <- vcovCL(VanDonkLBWOLS, cluster = ~code, type='HC1')

VanDonkVLBWOLS <- lm(
 vlbw ~ pmvandonk_cumulative  + 
                   temp_cumulative  + windspeed_cumulative + factor(religion_code) + dirty_cookingfuel+sex_child+urban+bmi+factor(wealth_index) + factor(anemic) + factor(region):factor(month_birth) + factor(year_birth) + birthorder + age_birth+ factor(caste),
  data = FinalDatasetVanDonk
)


cluster_seVanDonkVLBWOLS <- vcovCL(VanDonkVLBWOLS, cluster = ~code, type='HC1')



stargazer(
  VanDonkBWOLS, VanDonkLBWOLS, VanDonkVLBWOLS,
  se = list(sqrt(diag(cluster_seVanDonkBWOLS)),sqrt(diag(cluster_seVanDonkLBWOLS)),sqrt(diag(cluster_seVanDonkVLBWOLS))),digits=5,
  type = "text", omit='factor',
  title = "Second-Stage Regression with Clustered SE at District Level"
)
```



#Robustness excluding MOB, MOB+1 AND MOB+2 And re-estimating
```{r}


FinalDataset <- FinalDataset %>%
  mutate(
    northsharepreg_exMOB = (North_share1 + North_share2 + North_share3 + North_share4 + 
                            North_share5 + North_share6 + North_share7 + North_share8 + North_share9) / 9,
    
    southsharepreg_exMOB = (South_share1 + South_share2 + South_share3 + South_share4 + 
                            South_share5 + South_share6 + South_share7 + South_share8 + South_share9) / 9,
    
    eastsharepreg_exMOB  = (East_share1 + East_share2 + East_share3 + East_share4 + 
                            East_share5 + East_share6 + East_share7 + East_share8 + East_share9) / 9,
    
    windpreg_exMOB = (avg_wind_speed1 + avg_wind_speed2 + avg_wind_speed3 + avg_wind_speed4 + 
                      avg_wind_speed5 + avg_wind_speed6 + avg_wind_speed7 + avg_wind_speed8 + avg_wind_speed9) / 9,
    
    temppreg_exMOB = (avg_temperature1 + avg_temperature2 + avg_temperature3 + avg_temperature4 + 
                      avg_temperature5 + avg_temperature6 + avg_temperature7 + avg_temperature8 + avg_temperature9) / 9,
    
    pmpreg_exMOB = (pm1 + pm2 + pm3 + pm4 + pm5 + pm6 + pm7 + pm8 + pm9) / 9
  )


first_stage_preg_exMOB <- lm(
  pmpreg_exMOB ~ northsharepreg_exMOB:factor(region) +
    eastsharepreg_exMOB:factor(region) +
    southsharepreg_exMOB:factor(region) +
    temppreg_exMOB + windpreg_exMOB +
    religion + minoritycastetribe + cooking + female + urban +
    bmi + wealth_index + anemia +
    factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)


FinalDataset$preg_hat_exMOB <- predict(first_stage_preg_exMOB)


instr_vars_preg <- grep("northsharepreg_exMOB|eastsharepreg_exMOB|southsharepreg_exMOB", 
                        names(coef(first_stage_preg_exMOB)), value = TRUE)

vcov_clustered_preg <- vcovCL(first_stage_preg_exMOB, cluster = ~district_matched, type = "HC1")
f_test_clustered_preg <- linearHypothesis(first_stage_preg_exMOB, instr_vars_preg, vcov = vcov_clustered_preg)
f_stat_clustered_preg <- f_test_clustered_preg$F[2]
print(f_test_clustered_preg)
print(paste("Clustered first-stage F-statistic:", round(f_stat_clustered_preg, 2)))

second_stage_bw <- lm(
  brthwt ~ preg_hat_exMOB + temppreg_exMOB + windpreg_exMOB +
    minoritycastetribe + religion + cooking + female + urban +
    bmi + wealth_index + anemia +
    factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

second_stage_lbw <- lm(
  LBW ~ preg_hat_exMOB + temppreg_exMOB + windpreg_exMOB +
    minoritycastetribe + religion + cooking + female + urban +
    bmi + wealth_index + anemia +
    factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

second_stage_vlbw <- lm(
  VLBW ~ preg_hat_exMOB + temppreg_exMOB + windpreg_exMOB +
    minoritycastetribe + religion + cooking + female + urban +
    bmi + wealth_index + anemia +
    factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)


se_bw <- sqrt(diag(vcovCL(second_stage_bw, cluster = ~district_matched, type = "HC1")))
se_lbw <- sqrt(diag(vcovCL(second_stage_lbw, cluster = ~district_matched, type = "HC1")))
se_vlbw <- sqrt(diag(vcovCL(second_stage_vlbw, cluster = ~district_matched, type = "HC1")))

stargazer(
  second_stage_bw, second_stage_lbw, second_stage_vlbw,
  type = "text",
  se = list(se_bw, se_lbw, se_vlbw), keep='preg_hat_exMOB',digits=5
)

```
```{r}
FinalDataset <- FinalDataset %>%
  mutate(
    northsharepreg_exmob_mob1 = (North_share2 + North_share3 + North_share4 + North_share5 + North_share6 + North_share7 + North_share8 + North_share9) / 8,
    southsharepreg_exmob_mob1 = (South_share2 + South_share3 + South_share4 + South_share5 + South_share6 + South_share7 + South_share8 + South_share9) / 8,
    eastsharepreg_exmob_mob1  = (East_share2 + East_share3 + East_share4 + East_share5 + East_share6 + East_share7 + East_share8 + East_share9) / 8,
    windpreg_exmob_mob1       = (avg_wind_speed2 + avg_wind_speed3 + avg_wind_speed4 + avg_wind_speed5 + avg_wind_speed6 + avg_wind_speed7 + avg_wind_speed8 + avg_wind_speed9) / 8,
    temppreg_exmob_mob1       = (avg_temperature2 + avg_temperature3 + avg_temperature4 + avg_temperature5 + avg_temperature6 + avg_temperature7 + avg_temperature8 + avg_temperature9) / 8,
    pmpreg_exmob_mob1         = (pm2 + pm3 + pm4 + pm5 + pm6 + pm7 + pm8 + pm9) / 8,

    northsharepreg_exmob_mob1_mob2 = (North_share3 + North_share4 + North_share5 + North_share6 + North_share7 + North_share8 + North_share9) / 7,
    southsharepreg_exmob_mob1_mob2 = (South_share3 + South_share4 + South_share5 + South_share6 + South_share7 + South_share8 + South_share9) / 7,
    eastsharepreg_exmob_mob1_mob2  = (East_share3 + East_share4 + East_share5 + East_share6 + East_share7 + East_share8 + East_share9) / 7,
    windpreg_exmob_mob1_mob2       = (avg_wind_speed3 + avg_wind_speed4 + avg_wind_speed5 + avg_wind_speed6 + avg_wind_speed7 + avg_wind_speed8 + avg_wind_speed9) / 7,
    temppreg_exmob_mob1_mob2       = (avg_temperature3 + avg_temperature4 + avg_temperature5 + avg_temperature6 + avg_temperature7 + avg_temperature8 + avg_temperature9) / 7,
    pmpreg_exmob_mob1_mob2         = (pm3 + pm4 + pm5 + pm6 + pm7 + pm8 + pm9) / 7
  )

first_stage_exmob_mob1 <- lm(
  pmpreg_exmob_mob1 ~ northsharepreg_exmob_mob1:factor(region) +
    eastsharepreg_exmob_mob1:factor(region) +
    southsharepreg_exmob_mob1:factor(region) +
    temppreg_exmob_mob1 + windpreg_exmob_mob1 +
    religion + minoritycastetribe + cooking + female + urban +
    bmi + wealth_index + anemia +
    factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

FinalDataset$preg_hat_exmob_mob1 <- predict(first_stage_exmob_mob1)

instr_vars_exmob_mob1 <- grep("northsharepreg_exmob_mob1|eastsharepreg_exmob_mob1|southsharepreg_exmob_mob1", names(coef(first_stage_exmob_mob1)), value = TRUE)
vcov_cl_exmob_mob1 <- vcovCL(first_stage_exmob_mob1, cluster = ~district_matched, type = "HC1")
f_test_exmob_mob1 <- linearHypothesis(first_stage_exmob_mob1, instr_vars_exmob_mob1, vcov = vcov_cl_exmob_mob1)
f_stat_exmob_mob1 <- f_test_exmob_mob1$F[2]

first_stage_exmob_mob1_mob2 <- lm(
  pmpreg_exmob_mob1_mob2 ~ northsharepreg_exmob_mob1_mob2:factor(region) +
    eastsharepreg_exmob_mob1_mob2:factor(region) +
    southsharepreg_exmob_mob1_mob2:factor(region) +
    temppreg_exmob_mob1_mob2 + windpreg_exmob_mob1_mob2 +
    religion + minoritycastetribe + cooking + female + urban +
    bmi + wealth_index + anemia +
    factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

FinalDataset$preg_hat_exmob_mob1_mob2 <- predict(first_stage_exmob_mob1_mob2)

instr_vars_exmob_mob1_mob2 <- grep("northsharepreg_exmob_mob1_mob2|eastsharepreg_exmob_mob1_mob2|southsharepreg_exmob_mob1_mob2", names(coef(first_stage_exmob_mob1_mob2)), value = TRUE)
vcov_cl_exmob_mob1_mob2 <- vcovCL(first_stage_exmob_mob1_mob2, cluster = ~district_matched, type = "HC1")
f_test_exmob_mob1_mob2 <- linearHypothesis(first_stage_exmob_mob1_mob2, instr_vars_exmob_mob1_mob2, vcov = vcov_cl_exmob_mob1_mob2)
f_stat_exmob_mob1_mob2 <- f_test_exmob_mob1_mob2$F[2]

second_bw_exmob_mob1 <- lm(brthwt ~ preg_hat_exmob_mob1 + temppreg_exmob_mob1 + windpreg_exmob_mob1 +
                              minoritycastetribe + religion + cooking + female + urban + bmi + wealth_index + anemia +
                              factor(region):factor(MOB) + factor(YOB) + bord + age_birth, data = FinalDataset)

second_lbw_exmob_mob1 <- lm(LBW ~ preg_hat_exmob_mob1 + temppreg_exmob_mob1 + windpreg_exmob_mob1 +
                               minoritycastetribe + religion + cooking + female + urban + bmi + wealth_index + anemia +
                               factor(region):factor(MOB) + factor(YOB) + bord + age_birth, data = FinalDataset)

second_vlbw_exmob_mob1 <- lm(VLBW ~ preg_hat_exmob_mob1 + temppreg_exmob_mob1 + windpreg_exmob_mob1 +
                                minoritycastetribe + religion + cooking + female + urban + bmi + wealth_index + anemia +
                                factor(region):factor(MOB) + factor(YOB) + bord + age_birth, data = FinalDataset)

second_bw_exmob_mob1_mob2 <- lm(brthwt ~ preg_hat_exmob_mob1_mob2 + temppreg_exmob_mob1_mob2 + windpreg_exmob_mob1_mob2 +
                                   minoritycastetribe + religion + cooking + female + urban + bmi + wealth_index + anemia +
                                   factor(region):factor(MOB) + factor(YOB) + bord + age_birth, data = FinalDataset)

second_lbw_exmob_mob1_mob2 <- lm(LBW ~ preg_hat_exmob_mob1_mob2 + temppreg_exmob_mob1_mob2 + windpreg_exmob_mob1_mob2 +
                                    minoritycastetribe + religion + cooking + female + urban + bmi + wealth_index + anemia +
                                    factor(region):factor(MOB) + factor(YOB) + bord + age_birth, data = FinalDataset)

second_vlbw_exmob_mob1_mob2 <- lm(VLBW ~ preg_hat_exmob_mob1_mob2 + temppreg_exmob_mob1_mob2 + windpreg_exmob_mob1_mob2 +
                                     minoritycastetribe + religion + cooking + female + urban + bmi + wealth_index + anemia +
                                     factor(region):factor(MOB) + factor(YOB) + bord + age_birth, data = FinalDataset)



se_bw_exmob_mob1 <- sqrt(diag(vcovCL(second_bw_exmob_mob1, cluster = ~district_matched, type = "HC1")))
se_lbw_exmob_mob1 <- sqrt(diag(vcovCL(second_lbw_exmob_mob1, cluster = ~district_matched, type = "HC1")))
se_vlbw_exmob_mob1 <- sqrt(diag(vcovCL(second_vlbw_exmob_mob1, cluster = ~district_matched, type = "HC1")))

se_bw_exmob_mob1_mob2 <- sqrt(diag(vcovCL(second_bw_exmob_mob1_mob2, cluster = ~district_matched, type = "HC1")))
se_lbw_exmob_mob1_mob2 <- sqrt(diag(vcovCL(second_lbw_exmob_mob1_mob2, cluster = ~district_matched, type = "HC1")))
se_vlbw_exmob_mob1_mob2 <- sqrt(diag(vcovCL(second_vlbw_exmob_mob1_mob2, cluster = ~district_matched, type = "HC1")))

stargazer(
  second_bw_exmob_mob1, second_lbw_exmob_mob1, second_vlbw_exmob_mob1,
  type = "text",
  se = list(se_bw_exmob_mob1, se_lbw_exmob_mob1, se_vlbw_exmob_mob1),
  keep = "preg_hat_exmob_mob1",
  omit.stat = c("f", "ser"),
  column.labels = c("Birthweight", "LBW", "VLBW"),
  dep.var.labels = "Outcomes (Excl. MOB + 1)",
  digits = 5
)

stargazer(
  second_bw_exmob_mob1_mob2, second_lbw_exmob_mob1_mob2, second_vlbw_exmob_mob1_mob2,
  type = "text",
  se = list(se_bw_exmob_mob1_mob2, se_lbw_exmob_mob1_mob2, se_vlbw_exmob_mob1_mob2),
  keep = "preg_hat_exmob_mob1_mob2",
  omit.stat = c("f", "ser"),
  column.labels = c("Birthweight", "LBW", "VLBW"),
  dep.var.labels = "Outcomes (Excl. MOB + 1 + 2)",
  digits = 5
)


```


#Each year allowed to have different coefficient, differential impact of wind direction over years
```{r}
first_stageYear <- lm(
  tri_cumulative ~ avg_north_share_cumulative:factor(region):factor(YOB) +
                   avg_east_share_cumulative:factor(region):factor(YOB)  +   avg_south_share_cumulative:factor(region):factor(YOB)  + avg_wind_speed_cumulative +religion+minoritycastetribe+cooking+female+urban+bmi+wealth_index+ anemia + +avg_temperature_cumulative+ factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

# Save the predicted values of tri_cumulative
FinalDataset$tri_cumulative_hatYear <- predict(first_stageYear)


LBWYear <- lm(
  LBW ~ tri_cumulative_hatYear + avg_temperature_cumulative + avg_wind_speed_cumulative + minoritycastetribe + religion + cooking + female + urban + bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

VLBWYear <- lm(
  VLBW ~ tri_cumulative_hatYear + avg_temperature_cumulative + avg_wind_speed_cumulative + minoritycastetribe + religion + cooking + female + urban + bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)


stargazer(LBWYear,VLBWYear, type='text', omit='factor')
```

#Heterogeneity in wind direction by month in order to overcome Monotonicity issues
```{r}
first_stageMonth <- lm(
  tri_cumulative ~ avg_north_share_cumulative:factor(region):factor(MOB) +
                   avg_east_share_cumulative:factor(region):factor(MOB)  +   avg_south_share_cumulative:factor(region):factor(MOB)  + avg_wind_speed_cumulative +religion+minoritycastetribe+cooking+female+urban+bmi+wealth_index+ anemia + +avg_temperature_cumulative+ factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

# Save the predicted values of tri_cumulative
FinalDataset$tri_cumulative_hatMonth <- predict(first_stageMonth)


BWMonth <- lm(
  brthwt ~ tri_cumulative_hatMonth + avg_temperature_cumulative + avg_wind_speed_cumulative + minoritycastetribe + religion + cooking + female + urban + bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

LBWMonth <- lm(
  LBW ~ tri_cumulative_hatMonth + avg_temperature_cumulative + avg_wind_speed_cumulative + minoritycastetribe + religion + cooking + female + urban + bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

VLBWMonth <- lm(
  VLBW ~ tri_cumulative_hatMonth + avg_temperature_cumulative + avg_wind_speed_cumulative + minoritycastetribe + religion + cooking + female + urban + bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
  data = FinalDataset
)

stargazer(BWMonth, LBWMonth,VLBWMonth, type='text', omit='factor')
```



#Adding covariates/FE one by one
```{r}
#No Region*MonthFE
first_stageNoRMFE <- lm(
  tri_cumulative ~ avg_north_share_cumulative:factor(region) +
                   avg_east_share_cumulative:factor(region)  +   avg_south_share_cumulative:factor(region)  + 
                   avg_temperature_cumulative  + avg_wind_speed_cumulative +religion+minoritycastetribe+cooking+female+urban+bmi+wealth_index+ anemia + factor(YOB) + bord + age_birth,
  data = FinalDataset
)


# Save the predicted values of tri_cumulative
FinalDataset$tri_cumulative_hatNoRMFE <- predict(first_stageNoRMFE)

second_stageNoRMFE <- lm(
    brthwt ~ tri_cumulative_hatNoRMFE + avg_temperature_cumulative  + avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + factor(YOB) + bord + age_birth ,
  data = FinalDataset
)

# Calculate clustered standard errors at the district level
cluster_seNoRMFE <- vcovCL(second_stageNoRMFE, cluster = ~code, type='HC1')

# Display results with clustered standard errors
summary_clusteredNoRMFE <- coeftest(second_stageNoRMFE, vcov. = cluster_seNoRMFE)

# OLS counterpart
ols_NoRMFE <- lm(
  brthwt ~ tri_cumulative + avg_temperature_cumulative + avg_wind_speed_cumulative +
    religion + minoritycastetribe + cooking + female + urban + bmi + wealth_index +
    anemia + factor(YOB) + bord + age_birth,
  data = FinalDataset
)
cluster_se_ols_NoRMFE <- vcovCL(ols_NoRMFE, cluster = ~code, type = 'HC1')

# Stargazer output
stargazer(
  second_stageNoRMFE, ols_NoRMFE,
  se = list(sqrt(diag(cluster_seNoRMFE)), sqrt(diag(cluster_se_ols_NoRMFE))),
  type = "text", omit = 'factor',
  column.labels = c("IV", "OLS"),
  title = "2SLS vs OLS: No Region×Month Fixed Effects"
)

#No Demographic Covariates (only weather)

first_stageNoControls <- lm(
  tri_cumulative ~ avg_north_share_cumulative:factor(region) +
                   avg_east_share_cumulative:factor(region)  +   avg_south_share_cumulative:factor(region)  + 
                   avg_temperature_cumulative  + avg_wind_speed_cumulative + factor(region):factor(MOB) + factor(YOB),
  data = FinalDataset
)


# Save the predicted values of tri_cumulative
FinalDataset$tri_cumulative_hatNoControls <- predict(first_stageNoControls)

second_stageNoControls <- lm(
    brthwt ~ tri_cumulative_hatNoControls + avg_temperature_cumulative  + avg_wind_speed_cumulative + factor(YOB) + factor(region):factor(MOB) ,
  data = FinalDataset
)

# Calculate clustered standard errors at the district level
cluster_seNoControls <- vcovCL(second_stageNoControls, cluster = ~code, type='HC1')

# Display results with clustered standard errors
summary_clusteredNoControls <- coeftest(second_stageNoControls, vcov. = cluster_seNoControls)

# OLS counterpart
ols_NoControls <- lm(
  brthwt ~ tri_cumulative + avg_temperature_cumulative + avg_wind_speed_cumulative +
    factor(YOB) + factor(region):factor(MOB),
  data = FinalDataset
)
cluster_se_ols_NoControls <- vcovCL(ols_NoControls, cluster = ~code, type = 'HC1')

# Stargazer output
stargazer(
  second_stageNoControls, ols_NoControls,
  se = list(sqrt(diag(cluster_seNoControls)), sqrt(diag(cluster_se_ols_NoControls))),
  type = "text", omit = 'factor',
  column.labels = c("IV", "OLS"),
  title = "2SLS vs OLS: No Demographic Controls"
)


#No FEs at all
first_stageNoFE <- lm(
  tri_cumulative ~ avg_north_share_cumulative:factor(region) +
                   avg_east_share_cumulative:factor(region)  +   avg_south_share_cumulative:factor(region)  + 
                   avg_temperature_cumulative  + avg_wind_speed_cumulative +religion+minoritycastetribe+cooking+female+urban+bmi+wealth_index+ anemia + bord + age_birth,
  data = FinalDataset
)


# Save the predicted values of tri_cumulative
FinalDataset$tri_cumulative_hatNoFE <- predict(first_stageNoFE)

second_stageNoFE <- lm(
    brthwt ~ tri_cumulative_hatNoFE + avg_temperature_cumulative  + avg_wind_speed_cumulative +minoritycastetribe+religion+cooking+female+urban+bmi+wealth_index+anemia + bord + age_birth ,
  data = FinalDataset
)

# Calculate clustered standard errors at the district level
cluster_seNoFE <- vcovCL(second_stageNoFE, cluster = ~code, type='HC1')

# Display results with clustered standard errors
summary_clusteredNoFE <- coeftest(second_stageNoFE, vcov. = cluster_seNoFE)


# OLS counterpart
ols_NoFE <- lm(
  brthwt ~ tri_cumulative + avg_temperature_cumulative + avg_wind_speed_cumulative +
    religion + minoritycastetribe + cooking + female + urban + bmi + wealth_index +
    anemia + bord + age_birth,
  data = FinalDataset
)
cluster_se_ols_NoFE <- vcovCL(ols_NoFE, cluster = ~code, type = 'HC1')

# Stargazer output
stargazer(
  second_stageNoFE, ols_NoFE,
  se = list(sqrt(diag(cluster_seNoFE)), sqrt(diag(cluster_se_ols_NoFE))),
  type = "text", omit = 'factor',
  column.labels = c("IV", "OLS"),
  title = "2SLS vs OLS: No Fixed Effects"
)
#No YOB FE
# -------- FIRST STAGE --------
first_stage_RegionMonth_NoYOBFE <- lm(
  tri_cumulative ~ avg_north_share_cumulative:factor(region) +
                   avg_east_share_cumulative:factor(region) +
                   avg_south_share_cumulative:factor(region) +
                   avg_temperature_cumulative + avg_wind_speed_cumulative +
                   religion + minoritycastetribe + cooking + female + urban +
                   bmi + wealth_index + anemia + bord + age_birth +
                   factor(region):factor(MOB),  # keep Region×Month FE
  data = FinalDataset
)

FinalDataset$tri_cumulative_hat_RegionMonth_NoYOBFE <- predict(first_stage_RegionMonth_NoYOBFE)

# -------- SECOND STAGE IV --------
second_stage_RegionMonth_NoYOBFE <- lm(
  brthwt ~ tri_cumulative_hat_RegionMonth_NoYOBFE + avg_temperature_cumulative +
           avg_wind_speed_cumulative + religion + minoritycastetribe +
           cooking + female + urban + bmi + wealth_index + anemia +
           bord + age_birth + factor(region):factor(MOB),  # keep Region×Month FE
  data = FinalDataset
)
cluster_se_IV_RegionMonth_NoYOBFE <- vcovCL(second_stage_RegionMonth_NoYOBFE, cluster = ~code, type = 'HC1')

# -------- SIMPLE OLS --------
ols_RegionMonth_NoYOBFE <- lm(
  brthwt ~ tri_cumulative + avg_temperature_cumulative +
           avg_wind_speed_cumulative + religion + minoritycastetribe +
           cooking + female + urban + bmi + wealth_index + anemia +
           bord + age_birth + factor(region):factor(MOB),
  data = FinalDataset
)
cluster_se_ols_RegionMonth_NoYOBFE <- vcovCL(ols_RegionMonth_NoYOBFE, cluster = ~code, type = 'HC1')

# -------- STARGAZER TABLE --------
stargazer(
  second_stage_RegionMonth_NoYOBFE, ols_RegionMonth_NoYOBFE,
  se = list(sqrt(diag(cluster_se_IV_RegionMonth_NoYOBFE)), sqrt(diag(cluster_se_ols_RegionMonth_NoYOBFE))),
  type = "text", omit = 'factor',
  column.labels = c("IV", "OLS"),
  title = "2SLS vs OLS: Region×Month FE, No Year-of-Birth FE"
)


```



#Placebo Check: Randomizing Wind direction and doing 250 iterations (Not in code chunks as very time consuming to run, reinstate code chunks if you would like to see figures) 

``{r}


# Initialize result storage
placebo_results <- data.frame(
  Iteration = 1:250,
  Coef_brthwt_placebo = NA, StdErr_brthwt_placebo = NA, PValue_brthwt_placebo = NA,
  Coef_LBW_placebo = NA,    StdErr_LBW_placebo = NA,    PValue_LBW_placebo = NA,
  Coef_VLBW_placebo = NA,   StdErr_VLBW_placebo = NA,   PValue_VLBW_placebo = NA
)

# Set seed once for reproducibility
set.seed(7)
n <- nrow(FinalDataset)

for (i in 1:250) {
  # Shuffle observed wind shares
  FinalDataset$random_north_share <- sample(FinalDataset$avg_north_share_cumulative, n)
  FinalDataset$random_east_share  <- sample(FinalDataset$avg_east_share_cumulative, n)
  FinalDataset$random_south_share <- sample(FinalDataset$avg_south_share_cumulative, n)

  # First-stage regression with placebo instruments
  first_stage_placebo <- lm(
    tri_cumulative ~ random_north_share:factor(region) +
                     random_east_share:factor(region) +
                     random_south_share:factor(region) +
                     avg_temperature_cumulative + avg_wind_speed_cumulative +
                     religion + minoritycastetribe + cooking + female + urban +
                     bmi + wealth_index + anemia +
                     factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
    data = FinalDataset
  )

  # Predicted values from placebo instruments
  FinalDataset$tri_cumulative_hatplacebo <- predict(first_stage_placebo)

  ## Second-stage 1: brthwt
  second_stage_brthwt <- lm(
    brthwt ~ tri_cumulative_hatplacebo + avg_temperature_cumulative + avg_wind_speed_cumulative +
      minoritycastetribe + religion + cooking + female + urban +
      bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
    data = FinalDataset
  )
  cluster_se_brthwt <- vcovCL(second_stage_brthwt, cluster = ~code, type = "HC1")
  summary_brthwt <- coeftest(second_stage_brthwt, vcov. = cluster_se_brthwt)

  ## Second-stage 2: LBW
  second_stage_LBW <- lm(
    LBW ~ tri_cumulative_hatplacebo + avg_temperature_cumulative + avg_wind_speed_cumulative +
      minoritycastetribe + religion + cooking + female + urban +
      bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
    data = FinalDataset
  )
  cluster_se_LBW <- vcovCL(second_stage_LBW, cluster = ~code, type = "HC1")
  summary_LBW <- coeftest(second_stage_LBW, vcov. = cluster_se_LBW)

  ## Second-stage 3: VLBW
  second_stage_VLBW <- lm(
    VLBW ~ tri_cumulative_hatplacebo + avg_temperature_cumulative + avg_wind_speed_cumulative +
      minoritycastetribe + religion + cooking + female + urban +
      bmi + wealth_index + anemia + factor(region):factor(MOB) + factor(YOB) + bord + age_birth,
    data = FinalDataset
  )
  cluster_se_VLBW <- vcovCL(second_stage_VLBW, cluster = ~code, type = "HC1")
  summary_VLBW <- coeftest(second_stage_VLBW, vcov. = cluster_se_VLBW)

  ## Save placebo estimates
  placebo_results$Coef_brthwt_placebo[i]   <- summary_brthwt["tri_cumulative_hatplacebo", "Estimate"]
  placebo_results$StdErr_brthwt_placebo[i] <- summary_brthwt["tri_cumulative_hatplacebo", "Std. Error"]
  placebo_results$PValue_brthwt_placebo[i] <- summary_brthwt["tri_cumulative_hatplacebo", "Pr(>|t|)"]

  placebo_results$Coef_LBW_placebo[i]   <- summary_LBW["tri_cumulative_hatplacebo", "Estimate"]
  placebo_results$StdErr_LBW_placebo[i] <- summary_LBW["tri_cumulative_hatplacebo", "Std. Error"]
  placebo_results$PValue_LBW_placebo[i] <- summary_LBW["tri_cumulative_hatplacebo", "Pr(>|t|)"]

  placebo_results$Coef_VLBW_placebo[i]   <- summary_VLBW["tri_cumulative_hatplacebo", "Estimate"]
  placebo_results$StdErr_VLBW_placebo[i] <- summary_VLBW["tri_cumulative_hatplacebo", "Std. Error"]
  placebo_results$PValue_VLBW_placebo[i] <- summary_VLBW["tri_cumulative_hatplacebo", "Pr(>|t|)"]

  cat(sprintf("Iteration %d complete\n", i))
}

# Final results with placebo runs df
print(head(placebo_results))




``
#Plot from placebo check!
``{r}
ggplot(placebo_results,aes(x=Coef_brthwt_placebo)) + geom_histogram()

ggplot(placebo_results,aes(x=Coef_LBW_placebo)) + geom_histogram()

ggplot(placebo_results,aes(x=Coef_VLBW_placebo)) + geom_histogram()


``


``{r}

library(ggplot2)
library(dplyr)

placebo_plot_df <- placebo_results %>%
  mutate(
    index = row_number(),
    sig = ifelse(PValue_brthwt_placebo < 0.05, "p < 0.05", "p ≥ 0.05")
  )

ggplot(placebo_plot_df, aes(x = index, y = Coef_brthwt_placebo, color = sig)) +
  geom_point(size = 2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50",linewidth=1.1) +
  geom_hline(yintercept = -2.2, linetype = "dashed", color = "blue", linewidth = 1.1) +
  scale_color_manual(values = c("p < 0.05" = "red", "p ≥ 0.05" = "black")) +
  labs(
    x = "Placebo iteration",
    y = "Placebo BW Coefficient",
    color = "Significance"
  ) + theme_minimal() +
  theme(
    axis.title.x = element_text(face = "bold"),
    axis.title.y = element_text(face = "bold")
  )


``

``{r}
placebo_plot_lbw <- placebo_results %>%
  mutate(
    index = row_number(),
    sig = ifelse(PValue_LBW_placebo < 0.05, "p < 0.05", "p ≥ 0.05")
  )

ggplot(placebo_plot_lbw, aes(x = index, y = Coef_LBW_placebo, color = sig)) +
  geom_point(size = 2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50", linewidth=1.1) +
  geom_hline(yintercept = 0.002, linetype = "dashed", color = "blue", linewidth = 1) +
  scale_color_manual(values = c("p < 0.05" = "red", "p ≥ 0.05" = "black")) +
  labs( x = "Placebo iteration",
    y = "Placebo LBW Coefficient",
    color = "Significance"
  ) + theme_minimal() +
  theme(
    axis.title.x = element_text(face = "bold"),
    axis.title.y = element_text(face = "bold")
  )

``
``{r}
placebo_plot_vlbw <- placebo_results %>%
  mutate(
    index = row_number(),
    sig = ifelse(PValue_VLBW_placebo < 0.05, "p < 0.05", "p ≥ 0.05")
  )

ggplot(placebo_plot_vlbw, aes(x = index, y = Coef_VLBW_placebo, color = sig)) +
  geom_point(size = 2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50", linewidth=1.1) +
  geom_hline(yintercept = 0.00050, linetype = "dashed", color = "blue", linewidth = 1.1) +
  scale_color_manual(values = c("p < 0.05" = "red", "p ≥ 0.05" = "black")) +
  labs(
    x = "Placebo iteration",
    y = "Placebo VLBW Coefficient",
    color = "Significance"
  ) +
  theme_minimal()

``
#Code on how to make predicted vs actual pollution for regions and region*seasons full PDF
```{r}



# =========================
# 1) DATA: seasons
# =========================

df_season <- FinalDataset %>%
  filter(region %in% 29:0, MOB %in% 1:12) %>%
  mutate(
    season = case_when(
      MOB %in% 1:3   ~ "Jan–Mar",
      MOB %in% 4:6   ~ "Apr–Jun",
      MOB %in% 7:9   ~ "Jul–Sep",
      MOB %in% 10:12 ~ "Oct–Dec"
    ),
    region = factor(region, levels = 29:0)
  ) %>%
  select(region, season, tri_cumulative_hat, tri_cumulative) %>%
  pivot_longer(
    cols = c(tri_cumulative_hat, tri_cumulative),
    names_to = "type",
    values_to = "pm25"
  ) %>%
  mutate(
    type = dplyr::recode(
      type,
      "tri_cumulative_hat" = "Predicted (IV)",
      "tri_cumulative"     = "Actual"
    )
  )

# =========================
# 2) DATA: overall as extra facet
# =========================

df_overall <- FinalDataset %>%
  filter(region %in% 29:0, MOB %in% 1:12) %>%
  mutate(
    season = "Overall",
    region = factor(region, levels = 29:0)
  ) %>%
  select(region, season, tri_cumulative_hat, tri_cumulative) %>%
  pivot_longer(
    cols = c(tri_cumulative_hat, tri_cumulative),
    names_to = "type",
    values_to = "pm25"
  ) %>%
  mutate(
    type = dplyr::recode(
      type,
      "tri_cumulative_hat" = "Predicted (IV)",
      "tri_cumulative"     = "Actual"
    )
  )

# combine seasonal + overall facets
df_long_full <- bind_rows(df_season, df_overall) %>%
  mutate(
    season = factor(
      season,
      levels = c("Jan–Mar", "Apr–Jun", "Jul–Sep", "Oct–Dec", "Overall")
    )
  )

# =========================
# 3) Quantiles: only for Overall facet
# =========================

df_quants_overall <- df_long_full %>%
  filter(season == "Overall") %>%
  group_by(region, type) %>%
  summarise(
    q25 = quantile(pm25, 0.25, na.rm = TRUE),
    q50 = quantile(pm25, 0.50, na.rm = TRUE),
    q75 = quantile(pm25, 0.75, na.rm = TRUE),
    .groups = "drop"
  )

# =========================
# 3b) ONE SUMMARY BOX PER REGION
# =========================

df_labels <- df_quants_overall %>%
  tidyr::pivot_longer(
    cols      = c(q25, q50, q75),
    names_to  = "quantile",
    values_to = "value"
  ) %>%
  mutate(
    quantile = dplyr::recode(
      quantile,
      "q25" = "25th",
      "q50" = "50th",
      "q75" = "75th"
    )
  ) %>%
  group_by(region) %>%
  summarise(
    label = paste0(
      "Predicted (IV):\n",
      "  25th: ", sprintf("%.1f", value[type == "Predicted (IV)" & quantile == "25th"]), "\n",
      "  50th: ", sprintf("%.1f", value[type == "Predicted (IV)" & quantile == "50th"]), "\n",
      "  75th: ", sprintf("%.1f", value[type == "Predicted (IV)" & quantile == "75th"]), "\n\n",
      "Actual:\n",
      "  25th: ", sprintf("%.1f", value[type == "Actual" & quantile == "25th"]), "\n",
      "  50th: ", sprintf("%.1f", value[type == "Actual" & quantile == "50th"]), "\n",
      "  75th: ", sprintf("%.1f", value[type == "Actual" & quantile == "75th"])
    ),
    season = "Overall",
    x = Inf,
    y = Inf,
    hjust = 1.1,
    vjust = 1.1,
    .groups = "drop"
  )

# =========================
# 4) Plot base + paginate
# =========================

ncol <- 4  # 4 regions per page
nrow <- 5

p_base <- ggplot(df_long_full, aes(x = pm25, color = type, linetype = type)) +
  geom_density(size = 0.7, adjust = 1, na.rm = TRUE) +

  # quantile dots (still included)
  geom_point(
    data = df_quants_overall %>%
      tidyr::pivot_longer(
        cols      = c(q25, q50, q75),
        names_to  = "quantile",
        values_to = "pm25"
      ) %>%
      mutate(
        quantile = dplyr::recode(
          quantile,
          "q25" = "25th",
          "q50" = "50th",
          "q75" = "75th"
        ),
        season = "Overall"
      ),
    aes(
      x     = pm25,
      y     = 0,
      shape = quantile,
      color = type
    ),
    size        = 1.6,
    inherit.aes = FALSE
  ) +

  # ONE box per region (clean)
  geom_label(
    data = df_labels,
    aes(x = x, y = y, label = label, hjust = hjust, vjust = vjust),
    fill        = "white",
    label.size  = 0.3,
    size        = 2.6,
    alpha       = 0.85,
    inherit.aes = FALSE
  ) +

  theme_minimal(base_size = 12) +
  labs(
    title = expression(bold("Predicted vs. Actual PM2.5 by Region (4 Seasons + Overall)")),
    x     = "PM2.5 (μg/m³)",
    y     = "Density"
  ) +
  theme(
    legend.position      = "bottom",
    panel.grid.minor     = element_blank(),
    panel.grid.major.x   = element_blank()
  )

# count pages
p_first <- p_base + ggforce::facet_grid_paginate(
  season ~ region,
  ncol   = ncol,
  nrow   = nrow,
  page   = 1,
  scales = "free_x"
)
n_pages <- ggforce::n_pages(p_first)

# =========================
# 5) PDF output (title only on first page)
# =========================

pdf("pm25_region_SeasonAndOverall_ONEBOX.pdf", width = 10, height = 10)

for (i in 1:n_pages) {

  if (i == 1) {
    # First page: keep title
    p_out <- p_base
  } else {
    # Other pages: remove title
    p_out <- p_base + theme(plot.title = element_blank())
  }

  print(
    p_out +
      ggforce::facet_grid_paginate(
        season ~ region,
        ncol   = ncol,
        nrow   = nrow,
        page   = i,
        scales = "free_x"
      )
  )
}

dev.off()


```


#using fixest package (same as baseline) | Same results
```{r}

iv_mod_rmBW <- feols(
  birthweight ~ temp_cumulative + windspeed_cumulative + i(religion_code) +
    dirty_cookingfuel + sex_child + urban + bmi + i(wealth_index) + i(anemic) +
    birthorder + age_birth + i(caste) |
    region^month_birth + year_birth |
   pm_cumulative  ~ i(region, North_share_cumulative) +
               i(region, East_share_cumulative) +
               i(region, South_share_cumulative),
  data = FinalDataset,
  vcov = ~ district_matched
)


iv_mod_rmLBW <- feols(
  lbw ~ temp_cumulative + windspeed_cumulative + i(religion_code) +
    dirty_cookingfuel + sex_child + urban + bmi + i(wealth_index) + i(anemic) +
    birthorder + age_birth + i(caste) |
    region^month_birth + year_birth |
   pm_cumulative  ~ i(region, North_share_cumulative) +
               i(region, East_share_cumulative) +
               i(region, South_share_cumulative),
  data = FinalDataset,
  vcov = ~ district_matched
)



iv_mod_rmVLBW <- feols(
  vlbw ~ temp_cumulative + windspeed_cumulative + i(religion_code) +
    dirty_cookingfuel + sex_child + urban + bmi + i(wealth_index) + i(anemic) +
    birthorder + age_birth + i(caste) |
    region^month_birth + year_birth |
   pm_cumulative  ~ i(region, North_share_cumulative) +
               i(region, East_share_cumulative) +
               i(region, South_share_cumulative),
  data = FinalDataset,
  vcov = ~ district_matched
)



summary(iv_mod_rmBW)
summary(iv_mod_rmLBW)
summary(iv_mod_rmVLBW)

```
